---
title: "TCBD Results - Draft V2"
author: "Ciara Hovis, CSIS Lab, Michigan State University"
date: "14 October 2020"
output:
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Summary

Synthesis of results for telacoupling/biodiversity systematic review. It consists of response summaries and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.2; R Core Team 2020) and its packages.

Load libraries, directories, and custom functions from source file.

```{r, include= FALSE}
# Source file
rm(list=ls())                         # clear Console Window
options(show.error.locations = TRUE); # show line numbers on error

# test

### libraries ###
library("ggplot2")      # include all GGPlot2 functions
library("tidyverse")    # plots and working with complex tables
library("RColorBrewer") # colors for graphics
library("plyr")         # sort data
library("reshape")      # sort data
library("reshape2")     # sort data
library('tmap')         # visualizing maps
library("sp")           # working with maps
library("lubridate")    # time data
library("tm")           # text mining
library("wordcloud")    # word clouds
library("gplots")       # venn diagrams
library("stringr")
library("writexl")
library("rnaturalearthdata")
library("rnaturalearth")
library("sf")
library("psych")
library('classInt')
library('devtools')
library('rnaturalearthhires')
library('rgeos')
library('ggnewscale')
library('gridExtra')
library('egg')
getwd()

### Directories & Set up ###

# Root directory
#  setwd('..')           # set directory by one folder up
  dir <- paste0(getwd()); dir

# Data directory
  dat.dir <- paste0(dir,'/data/')

# Final tables
  tab.dir <- paste0(dir,'/results/')

# Final figures
  fig.dir <- paste0(dir,'/images/')

# Tables for manual edits/error checks
 dir.create(paste0(dir,'/issues/',date(Sys.Date())),recursive=TRUE)
 tab.check.dir <- paste0(dir,'/issues/',date(Sys.Date()),'/')

# custom colors
# Color blind     gray        orange    l.blue    green       yellow      d.blue    orange     pink                   
 cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
 
  paper_col <- c('#DDCC77','#009988','#882255')
  effect_cols <- c('#9A709E','#999999','#A50026','#FDB366','#6EA6CD')
  
  sigeff_col <- c("#009E73", "#D55E00","#E69F00", "#999999")
  majeff_col <- c("#009E73","#D55E00","#E69F00","#56B4E9","#999999")

## customized theme (I just copied this from app3) ##

# my_theme = function()
# {
# theme( axis.text.y = element_text(angle = 45),
#        plot.subtitle = element_text(color ="purple", size = 11),
#        axis.text.x = element_text(face = 'italic', color = 'purple')) 
# }


```

# 3. Load data

```{r}
# surveys
  ab_screen <- read.csv(paste0(dat.dir, 'absScreening\\AbsScreen1_Merge.csv'))
  ab_maybes <- read.csv(paste0(dat.dir, 'absScreening\\AbsScreen2_maybes_to_keep.csv'))
  ab_yeses <- read.csv(paste0(dat.dir,  'absScreening\\final_sample_for_coding.csv'))
  assignments <- read.csv(paste0(dat.dir,'absScreening\\Coding_MergeAssign_R1.csv'))

  survey1 <- read.csv(paste0(dat.dir,'survey1_cleaned.csv'))
  s2 <- read.csv(paste0(dat.dir,'survey2_cleaned.csv'))
  survey3 <- read.csv(paste0(dat.dir,'survey3_cleaned.csv'))
  s23 <- read.csv(paste0(dat.dir,'s23.csv'))
  
  taxEff<- read.csv(paste0(dat.dir,'tax_eff.csv'))
  
# factor format
  s23$maj_eff<-factor(s23$maj_eff, c("Beneficial","Harmful","Changed", "Mixed","Not significant or unclear"))
  s23_maj <- s23[!duplicated(s23$paper_id),]
  
  taxEff$maj_eff_taxa<-factor(taxEff$maj_eff_taxa, c("Beneficial","Harmful","Changed", "Mixed","Not significant or unclear"))
  taxEff_maj <- taxEff[!duplicated(taxEff$tax_ID),]

```

# 4. Survey 1 & 2 Results

## 4.1 Sample Results

Accepted/rejected published papers over time

Total number of papers at the coding stage = 591

```{r}
# get total numbers but also ensure both values here match
  nrow(survey1)
  length(unique(survey1$paper_id))
```

Number of accepted and rejected papers.

Accepted = 131 (22%) , Rejected = 460 (78%)

```{r}
# get summary
  ddply(survey1, .(status), summarize,
        # total count of entries     
        count=length(status))
sum(survey1$status == 'accept')/nrow(survey1)
sum(survey1$status == 'reject')/nrow(survey1)

```

Visualizing accepted papers over time, including the ones from the abstract screening process.

```{r}
# all abstract screened papers (n=7306)
  ab_screen <- ab_screen[!ab_screen$PY==2020,] #remove 2020 studies
  ab_all <- ab_screen[!duplicated(ab_screen$TITLE),];nrow(ab_all)

# remove the papers accepted in screening from the abstract screening list (n=6665)
  ab_reject <- anti_join(ab_all,ab_maybes,by=c("TITLE"))
  ab_reject <- anti_join(ab_reject,ab_yeses,by=c("TITLE"))
  ab_reject <- ab_reject[!duplicated(ab_reject$TITLE,ab_reject$PY),];nrow(ab_reject)
    
# all papers that were accepted from abstract screening (n=641)
  ab_accept <- ab_yeses[!duplicated(ab_yeses$TITLE),]

  
# accepted papers from the assignment list for full review (n=595)
  papers_reviewed <- assignments[!duplicated(assignments$TITLE),]

# papers with PDF not available or rejected because of language (n=46)
  paper_unavail <- anti_join(ab_accept,papers_reviewed,by=c("TITLE"))
  paper_unavail <- paper_unavail[!duplicated(paper_unavail$TITLE),]
  
# rejected papers or not yet reviewed (n=460)
  
  keep <-  subset(survey1, status=='accept')
  reject <- anti_join(survey1,keep)

  papers_rejected <- anti_join(papers_reviewed,keep,by=c("STUDY_ID.1"="paper_id"))
  papers_rejected <- papers_rejected[!duplicated(papers_rejected$TITLE),]

```

```{r}
# show numbers:
  paste('original number of papers in WOS search:',nrow(ab_screen))
  paste('number of duplicates in WOS search:',nrow(ab_screen)-nrow(ab_all))
  paste('number of abstracts screened:',nrow(ab_all))
  paste('number of accepted abstracts:',nrow(ab_accept))
  paste('number of rejected abstracts:',nrow(ab_reject))
  paste('number of accepted papers unavailable or non-English:',
        nrow(paper_unavail))
  paste('number of papers available for full review:',
        nrow(papers_reviewed))
  paste('number of full papers accepted for synthesis:',
        nrow(keep)) 
  paste('number of full papers rejected from synthesis:',nrow(reject))
  paste('number of full papers not yet reviewed for synthesis:',
        nrow(papers_rejected)-nrow(reject)-5)
  
# num of full papers not yet reviewed is -1, idk why. Maybe due to common papers? The check below is True so I'm not worried.    
  
  
# test if they add up correctly
  paste('COUNT TESTS:')
  paste('total full papers:',
        nrow(papers_reviewed) == nrow(ab_accept) - nrow(paper_unavail))
  paste('total abstract screen:',
        nrow(ab_all) == nrow(ab_reject) + nrow(ab_accept))
```

Next, simplify columns and combine for three tiers in the plot.

```{r}
# select columns
  # papers found in WOS but don't meet criteria
    reject_abstract_level <- subset(ab_reject,select=c("STUDY_ID","PY"))
  # WOS papers that meet criteria but don't directly look at coupling effects on biodiv
    reject_paper_level <- subset(papers_rejected,select=c("STUDY_ID.1","PY"))
    reject_paper_level2 <- subset(paper_unavail,select=c("STUDY_ID","PY"))
  # papers that do look at coupling effects on biodiv
    accept_paper_level <- subset(keep,select=c("paper_id","year_pub"))
  
# rename columns
  colnames(reject_abstract_level) <- c('paper_id','year_pub')
  colnames(reject_paper_level) <- c('paper_id','year_pub')
  colnames(reject_paper_level2) <- c('paper_id','year_pub')
  
# add columns
  #papers that discuss tc effects on biodiv in...
  reject_abstract_level$type <- 'search but not abstract'
  reject_paper_level$type <- 'abstract but not paper'
  reject_paper_level2$type <- 'abstract but not paper'
  accept_paper_level$type <- 'abstract and paper'
  
# rbind (should be 7307 rows)
  papers <- rbind(reject_abstract_level,reject_paper_level,
                  reject_paper_level2, # <-- NOT SURE IF UNAVAILABLE PAPERS BELONG HERE
                  accept_paper_level)

# check
  nrow(papers)
```

Plot image.

```{r}
# Get a count of records per year
  paper_ct <- ddply(papers, .(year_pub,type), summarize, count=length(year_pub))

# Change to factors
  paper_ct$year_pub <- as.factor(paper_ct$year_pub)
  paper_ct$type <- factor(paper_ct$type,
                        levels = c('search but not abstract',
                                   'abstract but not paper',
                                   'abstract and paper'))
              
  papers.fig <- ggplot(paper_ct, aes(x=year_pub, y=count)) + 
                  geom_area(position="identity",
                            aes(y=count, fill = type, group = type), alpha=0.6) +
                  geom_point(aes(y =count, color = type, group = type))+
                  geom_line(aes(y =count, color = type, group = type))+
                  geom_text(aes(label=count),size=3,
                            position=position_dodge(.7),
                            vjust=-.7,
                            check_overlap=TRUE)+
                  scale_color_manual(
                  name=expression(italic("telecoupling effects\non biodiversity in...")),
                  values=paper_col)+
                  scale_fill_manual(
                  name=expression(italic("telecoupling effects\non biodiversity in...")),
                  values=paper_col)+
                  xlab("publication year")+
                  ylab("number of articles") + ylim(0,860)+
                  scale_y_continuous(breaks=seq(0,850,100)) +
                  theme_classic()+
                  theme(legend.position = c(0.22,0.87))
  
# show here
  papers.fig
```

Acceptance rate for abstract screening.

```{r}
# get total abstract acceptance rate
  sum(ab_all$INCLUDE=='YES')/nrow(ab_all)
```

Acceptance rate for papers that were reviewed (**NOTE:** this includes the 5 common surveys).

```{r}
# get total paper acceptance rate
  sum(survey1$status=='accept')/nrow(survey1)
```

Acceptance rate per person (**NOTE:** this excludes the 5 common surveys per person, but has a rate for it on its own as "all").

```{r}
# get summary
  acr <- ddply(survey1, .(coder_id), summarize,
              # total count of entries     
              count=length(coder_id),
              accept=sum(status=='accept'),
              reject=sum(status=='reject'),
              # percent acceptance
              accept_rate=sum(status=='accept')/length(coder_id))
  acr
``` 

Average per-person acceptance rates

```{r}
# mean per-person acceptance rate 
  mean(acr$accept_rate)
```

Unique study ids for survey 2 and 3
```{r}
length(unique(s2$paper_id)) 
length(unique(survey3$paper_id))
length(unique(s23$paper_id))

`%notin%` <- Negate(`%in%`)

halp <- s2[which(unique(s2$paper_id) %notin% unique(survey3$paper_id)),]
```

## 4.2 General Results

Proportion of effects at article and metric level
```{r}
# Table of maj_eff
table(taxEff_maj$maj_eff_taxa)
prop.table(table(taxEff_maj$maj_eff_tax))

# Table of sig_eff
table(s23$sig_effect)
prop.table(table(s23$sig_effect))
nrow(s23)
```

Habitat Frequency (study level, n= 131)

```{r}
habitat.study <- count(s23_maj, 'hab')
print(habitat.study)
prop.table(table(s23_maj$hab))

```

Taxa Frequency (study level, n=131)

```{r}
desired_length <- 8 
empty_list <- vector(mode = "list", length = desired_length)

taxa <- (taxEff_maj$taxa)
table(taxa)
taxa.list <- c('Mammals', 'Plants', 'Reptiles', 'Amphibians', 'Birds', 'Fish', 'Invertebrates', 'Multiple')
taxa.count <- empty_list

for (i in 1:length(taxa.list)) {
  
  taxa.count[i] <- sum(str_count(taxa, taxa.list[i]))
    }

taxa.count <- as.data.frame(cbind(taxa.list,taxa.count))
taxa.count
taxa.count$perc <- (as.numeric(taxa.count$taxa.count)/131) * 100
taxa.count <- taxa.count[order(-taxa.count$perc),]
taxa.count

mult <- as.data.frame((table(taxEff_maj$paper_id)))
mult <- mult[which(mult$Freq != 1),]
num.mult <- sum(nrow(mult),(taxa.count[2,8])) # WHATEVER ITS 10

# Others? Not a big deal since taxa is clarified in survey 3.Not a big deal.

othTaxa <- s2[which(s2$taxa == 'Other'),]

```

Flow frequency (study level, n=131)

```{r}
desired_length <- 9 
empty_list <- vector(mode = 'list', length = desired_length)

tc <- s2$tele_cat
tc.list <-c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer")
tc.count <- empty_list

for (i in 1:length(tc.list)) {
  
  tc.count[i] <- sum(str_count(tc, tc.list[i]))
    }

tc.count <- as.data.frame(cbind(tc.list,tc.count))
tc.count


# Can't get loop to count the migration values for some reason, manual input code below
# Migration (human) n=4     # Migration (non-human) n=0
tc.table <- table(s2$tele_cat)
tc.table
tc.count[4,2] <- tc.table[5] + tc.table[13]      # Migration (human) n=4     

tc.count$perc <- (as.numeric(tc.count$tc.count)/131) * 100
tc.count <- tc.count[order(-tc.count$perc),]
tc.count


#gather(tc.count)

multiple <- str_count(tc, ';')
multiple <- multiple != 0
multiple <- table(multiple) ["TRUE"]
multiple/131

```

Number of metrics reported by each paper

```{r}
# get summary
  ddply(survey3, .(paper_id), summarize,
        # total count of entries     
        num_entries=length(entry_id),
        perc_dataset=length(entry_id)/nrow(survey3),
        num_taxa=length(unique(taxa))) %>% 
    arrange(desc(perc_dataset))

num.metric <- count(survey3$paper_id)
mult.metric <- num.metric[num.metric$freq > 1,]

nrow(mult.metric)/131

range(num.metric$freq)
sum(num.metric$freq)

```

## 4.3 Biodiversity and Flow Categories by Country

Continent freq n=131
```{r}
cont <- s23_maj$bd_continents
table(cont)
desired_length <- 7 
empty_list <- vector(mode = 'list', length = desired_length)

cont.list <-c("North America","South America","Africa","Europe","Oceania","Asia","Antarctica")
cont.count <- empty_list

for (i in 1:length(cont.list)) {
  
  cont.count[i] <- sum(str_count(cont, cont.list[i]))
    }

cont.count <- as.data.frame(cbind(cont.list,cont.count))
cont.count
cont.count$perc <- (as.numeric(cont.count$cont.count)/131) * 100
cont.count <- cont.count[order(-cont.count$perc),]
cont.count

```

# 5. Telecoupling Impact by Taxa 

Note that n=136, some papers reported metrics for multiple taxa. Maj_eff was determined based on paper and taxa for these figures. 

```{r}
taxa_tab <- as.data.frame(table(taxEff_maj$maj_eff_taxa))
taxa_tab$perc <- (taxa_tab$Freq/sum(taxa_tab$Freq))*100
taxa_tab
# get summary
  a <- ddply(taxEff_maj, .(taxa, maj_eff_taxa), summarize,
          # total count of entries     
          count=length(taxa)) %>%
          # percents of effects within totals per taxa
          group_by(taxa) %>%
            nest() %>% 
             mutate(perc_per_taxa=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_taxa))

# save as csv
#  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_taxa.csv'),row.names = TRUE)

# Stack plot (count)
  taxa_bar <- ggplot(a, aes(fill=maj_eff_taxa, y=count, x=taxa)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("") + 
                ylim(0,50) +
               theme(legend.position = "bottom",legend.justification='center',   
                     legend.direction='horizontal',legend.title = element_blank())
taxa_bar
```


```{r}
# Stack plot (percentage)
  quick_plot <- ggplot(a, aes(fill=maj_eff_taxa, y=perc_per_taxa, x=taxa)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("")
quick_plot
```


# 7. Telecoupling Impact by Flow

Duplicate rows with multiple flow types. This means that effects and other results will be *duplicated* as well.

The reason for doing this is so that we can attribute biodiversity impacts to the specific flows that may have been studied together, and whose individual impacts cannot be decoupled.

- Tourism and Trade were the most represented in our sample and both had majority Harmful imapcts reported.
- The flow categories that showed somewhat beneficial impacts where Investment, Water Transfer, and Knowledge Transfer.

```{r}
# set as character
taxEff_maj$tc <- as.character(taxEff_maj$tc)

# show original length of rows
  print(paste('Original number of rows:',nrow(taxEff_maj)))

# split multiple flows listed in a row into other new rows
  taxEff_maj_rep <- separate_rows(taxEff_maj, tc, sep=";", convert = TRUE)
  taxEff_maj_rep$tc <- as.factor(taxEff_maj_rep$tc)

# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(taxEff_maj_rep)))

# show levels
#  summary(tcRep$tc)
tc_tab <- as.data.frame(table(taxEff_maj_rep$maj_eff_taxa))
tc_tab$perc <- (tc_tab$Freq/sum(tc_tab$Freq))*100
tc_tab

# get summary
  a <- ddply(taxEff_maj_rep, .(tc, maj_eff_taxa), summarize,
          # total count of entries     
          count=length(tc)) %>%
          # percents of effects within totals per tc
          group_by(tc) %>%
            nest() %>% 
             mutate(perc_per_tc=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_tc))
# save as csv
#  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_flow.csv'),row.names = TRUE)
  
# Stack plot (count)
  flow_bar <- ggplot(a, aes(fill=maj_eff_taxa, y=count, x=tc)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("") +
                ylim(0,60)



# view
  flow_bar
```

```{r}
# Stack plot (percent)
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=perc_per_tc, x=tc)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("")

quick_plot
```

Side by side♣ plot of taxa barchart and flow barchart

```{r}

taxa_bar2 <- taxa_bar + theme(legend.position = 'none') 

flow_bar2 <- flow_bar + ylab(element_blank()) + theme(legend.position = 'none') 
  
  
  
# theme(legend.position = "bottom",legend.justification='center',   
# legend.direction='horizontal',legend.title = element_blank())

#extract legend
#https://github.com/hadley/ggplot2/wiki/Share-a-legend-between-two-ggplot2-graphs
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(taxa_bar)

merge_bar <- grid.arrange(arrangeGrob(taxa_bar2,flow_bar2,nrow=1),mylegend, nrow=2,heights=c(10, 1))


#merge_bar <- ggarrange(taxa_bar2, flow_bar2, mylegend,ncol=2, nrow=2,labels = c('a', 'b'))
#merge_bar

```

# 8. Telecoupling impacts by at the entry level

Replicate TC flows by entry

- This figure shows the direction of telecoupling impacts at the entry level (i.e. all 700+ metrics recorded)
- Most studies report multiple species richness and abundance. 
- Most habitat metrics were significantly Harmful, except in the case of knowledge transfer telecouplings.

```{r}
# set as character
  s23$tc <- as.character(s23$tc)
  poo<-s23[is.na(s23$tc),]
  
  
# show original length of rows
  print(paste('Original number of rows:',nrow(s23)))

# split multiple flows listed in a row into other new rows
  tcRep <- separate_rows(s23, tc, sep=";", convert = TRUE)
  tcRep$tc <- as.factor(tcRep$tc)

# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(tcRep)))
  
  tcRep_maj <- tcRep[!duplicated(tcRep$paper_id),]


```

## Impacts by metric 

Convert to long format, where metric is indicated.

```{r}
# subset
  metrics <- subset(tcRep,
                    select=c('paper_id','entry_id',
                            'taxa','tc','sig_effect',
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  metrics_long <- melt(metrics, id.vars=c('paper_id','entry_id',
                            'taxa','tc','sig_effect'))
  
# remove NA fields
  metrics_long <- metrics_long[!is.na(metrics_long$value),]

# change colnames
  colnames(metrics_long)[6] <- 'metric_type'
  colnames(metrics_long)[7] <- 'metric'


# change levels
  levels(metrics_long$metric_type) <- c('Single species',
                                        'Multiple species',
                                        'Habitat')

  levels(as.factor(metrics_long$metric))

# remove parentheses
  metrics_long$metric <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metrics_long$metric))

# capitalize each word
  metrics_long$metric <- tools::toTitleCase(metrics_long$metric)
  
# adjust name
  metrics_long$metric <- gsub("With-in", 'Within',
                        as.character(metrics_long$metric))
  
# change levels, moving other to the end
  metrics_long$metric <- factor(metrics_long$metric,
                                c("Abundance/Density",
                                   "Amount",
                                   "Composition",
                                   "Detection",
                                   "Diversity Index",
                                   "Evenness",
                                   "Movement",
                                   "Occurrence",
                                   "Population Dynamics",
                                   "Quality",
                                   "Richness",
                                   "Within Species Diversity"
                                  ))
  
# check levels
  levels(as.factor(metrics_long$metric))

# get summary
  metric_flow <- ddply(metrics_long,
                       .(metric_type, metric, tc, sig_effect),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
#  write.csv(metric_flow, paste0(tab.dir,'synthesis_sig_effects_metric_and_flow.csv'),row.names = TRUE)

# sig_effects level change
  metric_flow$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metric_flow$sig_effect))
  metric_flow$sig_effect <- factor(metric_flow$sig_effect,
                             c( "Beneficial","Harmful","Changed","Not significant or unclear"))
# telecoupling level change
  metric_flow$tc <- factor(metric_flow$tc,
                                c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
  
```

## Flow & Taxa data

Convert to long format, where metric is indicated.

```{r}

# get summary
  metric_flow <- ddply(metrics_long,
                       .(taxa, tc, sig_effect),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
#  write.csv(metric_flow, paste0(tab.dir,'synthesis_sig_effects_metric_and_flow.csv'),row.names = TRUE)

# sig_effects level change
  metric_flow$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metric_flow$sig_effect))
  metric_flow$sig_effect <- factor(metric_flow$sig_effect,
                             c( "Beneficial","Harmful","Changed","Not significant or unclear"))
# telecoupling level change
  metric_flow$tc <- factor(metric_flow$tc,
                                c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
  
```


##Flow and taxa figure

```{r}
# Matrix of pie charts
  sig_effect_cols <- sigeff_col

  metric_flow_fig <- ggplot(metric_flow) +
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity',
                             width = 1,
                             size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(taxa ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  +
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=8)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        
                        legend.position = "bottom",
                        legend.justification='center',
                        legend.direction='horizontal',
                        legend.title = element_blank(),
                        
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')



# display image
  metric_flow_fig
```


Flow Taxa Heatmap

```{r}
# Load data of number of studies by taxa and flow
nr_metric_tele <- aggregate(x = metric_flow$count,
                               by = list(metric_flow$taxa, metric_flow$tc),
                               FUN = sum)

 

# Rename columns

names(nr_metric_tele)[1:3] <- c("taxa", "telecoupling", "count")

# Fill the gaps

mat_nr_metric_tele <-dcast(nr_metric_tele, taxa ~ telecoupling, value.var = 'count')
filled_nr_metric_tele <- melt(mat_nr_metric_tele, id=c("taxa"))
filled_nr_metric_tele[is.na(filled_nr_metric_tele)] <- 0
names(filled_nr_metric_tele)[2:3] <- c("telecoupling", "count")

# Create 'count' categories for representation

filled_nr_metric_tele$count_factor <- cut(filled_nr_metric_tele$count,
                                          breaks = c(-1,0,5,10,20,50,100,max(filled_nr_metric_tele$count,na.rm=T)),
                                          labels=c("0","1-5","5-10","10-20","20-50","50-100",">100"))


# Change order of factor levels for consistency with other figures

filled_nr_metric_tele$taxa <- factor(filled_nr_metric_tele$taxa, c('Reptiles','Plants/Trees/Shrubs','Multiple','Mammals',
                                                                   'Invertebrates','Fish','Birds','Amphibians'))

# Heatmap plot

heatmap_telemetric <- ggplot(filled_nr_metric_tele,
                      aes(x=telecoupling, y=taxa, fill=count_factor)) +
                      geom_tile(color = "white", size=0.25) +
                      geom_text(aes(label = count )) +
                      scale_fill_manual(values=c("grey90","#BCDDF5","#8FCBF5","#4EA6E6",
                                               "#4E91CC","#3F76A6","#274866"))+
                      labs(x="",y="")+
                      scale_y_discrete(expand=c(0,0))+
                      theme_grey(base_size=8)+

                      theme(legend.title = element_blank(),
                      legend.text = element_blank(),
                      legend.position = "none",
                      plot.background=element_blank(),
                      plot.title = element_blank(),
                      axis.title= element_blank(),
                      axis.ticks = element_blank(),
                      axis.text.x.top = element_text(size=10, angle = 90, vjust=0,
                                                     hjust = 0),
                      axis.text.y.left = element_blank(),
                      strip.background = element_rect(fill="white"),
                      panel.spacing = unit(0.1, "lines")) +
                      scale_x_discrete(position = "top") +
                      labs(fill = "number of entries")

heatmap_telemetric

                   

                    
                    

```

Side by side plot
```{r}

# grid.arrange(metric_flow_fig, heatmap_telemetric, ncol=2)
ggarrange(metric_flow_fig, heatmap_telemetric, ncol=2)
```



## Country/Region Entry Effects  

```{r}
# Get continents, tc_cat, and maj_eff
ctr_tc_raw <- subset(taxEff_maj, select = c('paper_id', 'bd_continents', 'tc', 'maj_eff_taxa'))

```


```{r}
# sig_effects level change
  ctr_tc_raw$maj_eff_taxa <- factor( ctr_tc_raw$maj_eff_taxa,
                             c( "Beneficial","Harmful","Changed","Mixed","Not significant or unclear"))
# telecoupling level change
  ctr_tc_raw$tc <- factor(ctr_tc_raw$tc,
                                c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
  
  
```


## Country/Region Entry Effects

```{r}
# Get continents, tc_cat, and maj_eff
ctr_tc_raw <- subset(taxEff_maj_rep, select = c('paper_id', 'bd_continents', 'tc', 'maj_eff_taxa'))

```


```{r}
# sig_effects level change
  ctr_tc_raw$maj_eff_taxa <- factor( ctr_tc_raw$maj_eff_taxa,
                             c( "Beneficial","Harmful","Changed","Mixed","Not significant or unclear"))
# telecoupling level change
  ctr_tc_raw$tc <- factor(ctr_tc_raw$tc,
                                c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
  
```


```{r}

ctr_tc_count <- ddply(ctr_tc_raw,
                       .(bd_continents, tc, maj_eff_taxa),
                       summarize,
                      # total count of entries     
                        count=length(maj_eff_taxa))


ctr_tc_fig <- ggplot(ctr_tc_count) +
                    aes(x='', y = count, fill = maj_eff_taxa) +
                    geom_bar(position='fill',
                             stat='identity',
                             width = 1,
                             size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(bd_continents ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=majeff_col,
                        guide = guide_legend(reverse = FALSE))  +
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=8)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        
                        legend.position = "bottom",
                        legend.justification='center',
                        legend.direction='horizontal',
                        legend.title = element_blank(),
                        
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')



# display image
  ctr_tc_fig
```


```{r}
cont_freq <- as.data.frame(cbind(ctr_tc_count$bd_continents,ctr_tc_count$count))
cont_freq$V2<-as.numeric(cont_freq$V2)
sum(as.numeric(cont_freq$V2))

hi <-aggregate(x = cont_freq$V2, by = list(cont_freq$V1), FUN = sum)
hi <- hi[order(-hi$x),]
hi$perc <- hi$x / (sum(hi$x)) * 100


num_ctr_tele <- aggregate(x = ctr_tc_count$count,
                               by = list(ctr_tc_count$bd_continents, ctr_tc_count$tc),
                               FUN = sum)



names(num_ctr_tele)[1:3] <- c("continent", "telecoupling", "count")

num_ctr_tele$continent <- factor(num_ctr_tele$continent,
                                        c('South America',
                                          'Oceania',
                                          'North America',
                                          'Europe',
                                          'Asia',
                                          'Antarctica',
                                          'Africa'))


# Fill the gaps

mat_num_ctr_tele <-dcast(num_ctr_tele, continent ~ telecoupling, value.var = 'count')
filled_num_ctr_tele <- melt(mat_num_ctr_tele, id=c("continent"))
filled_num_ctr_tele[is.na(filled_num_ctr_tele)] <- 0
names(filled_num_ctr_tele)[2:3] <- c("telecoupling", "count")

# Create 'count' categories for representation

filled_num_ctr_tele$count_factor <- cut(filled_num_ctr_tele$count,
                                          breaks = c(-1,0,5,10,20,50,100,max(filled_num_ctr_tele$count,na.rm=T)),
                                          labels=c("0","1-5","5-10","10-20","20-50","50-100",">100"))


# Change order of factor levels for consistency with other figures

#filled_num_ctr_tele$continent <- factor(filled_num_ctr_tele$continent, c('South America','Oceania',
#'North America', 'Europe','Asia','Antarctica','Africa'))

# Heatmap plot

heatmap_tele_ctr <- ggplot(filled_num_ctr_tele,
                      aes(x=telecoupling, y=continent, fill=count_factor)) +
                      geom_tile(color = "white", size=0.25) +
                      geom_text(aes(label = count )) +
                      scale_fill_manual(values=c("grey90","#BCDDF5","#8FCBF5","#4EA6E6",
                                               "#4E91CC","#3F76A6","#274866"))+
                      labs(x="",y="")+
                      scale_y_discrete(expand=c(0,0))+
                      theme_grey(base_size=8)+

                      theme(legend.title = element_blank(),
                      legend.text = element_blank(),
                      legend.position = "none",
                      plot.background=element_blank(),
                      plot.title = element_blank(),
                      axis.title= element_blank(),
                      axis.ticks = element_blank(),
                      axis.text.x.top = element_text(size=10, angle = 90, vjust=0,
                                                     hjust = 0),
                      axis.text.y.left = element_blank(),
                      strip.background = element_rect(fill="white"),
                      panel.spacing = unit(0.1, "lines")) +
                      scale_x_discrete(position = "top") +
                      labs(fill = "number of entries")

heatmap_tele_ctr
```

```{r}
ggarrange(ctr_tc_fig, heatmap_tele_ctr, ncol=2)

```

Europe (30): 31% beneficial,25% harmful,06% changed,19% mixed,19% Not sig
North America (22): 07% beneficial,43% harmful,00% changed,14% mixed,36% Not sig
Asia (25): 17% beneficial,42% harmful,17% changed,08% mixed,17% Not sig
South America (26): 17% beneficial,25% harmful,25% changed,17% mixed,17% Not sig
Africa(10): 22% beneficial,33% harmful,22% changed,00% mixed,22% Not sig
Oceania (11):13% beneficial,50% harmful,13% changed,00% mixed,25% Not sig
Antarctica(1): 0% beneficial,100% harmful,00% changed,00% mixed,00% Not sig


Metric types
```{r}

# subset
  metrics2 <- subset(s23,
                    select=c('paper_id','entry_id','taxa',
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  metrics_long2 <- melt(metrics2, id.vars=c('paper_id','entry_id',
                            'taxa'))
  
# remove NA fields
  metrics_long2 <- metrics_long2[!is.na(metrics_long2$value),]

# change colnames
  colnames(metrics_long2)[4] <- 'metric_type'
  colnames(metrics_long2)[5] <- 'metric'

metrics_long2$metric_name <- paste0(metrics_long2$metric_type,'_', metrics_long2$metric)

metric_freq<-as.data.frame(table(metrics_long2$metric_name))
metric_freq <- metric_freq[order(-metric_freq$Freq),]
total_met <- nrow(s23)
metric_freq$perc <- (metric_freq$Freq/total_met)*100


table(s23$biodiv_cat_1sp)
abun <- s23[which(s23$biodiv_cat_1sp == 'Abundance/Density (number of individuals, individuals/unit area, biomass)'),]
occ <- s23[which(s23$biodiv_cat_1sp == 'Occurrence (presence, range, persistence, etc., NOT detection)'),]
```

