---
title: "MCBD Results"
author: "Ciara Hovis, CSIS Lab, Michigan State University"
date: "6 October 2020 (Updated 7 Octobter 2020)"
output:
  word_document:
    toc: yes
    toc_depth: '4'
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Summary

Synthesis of survey 2 and 3 results for metacoupling/biodiversity systematic review. It consists of response summaries and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.2; R Core Team 2020) and its packages.

Load libraries, directories, and custom functions from source file.

```{r, include= FALSE}
# Source file
rm(list=ls())                         # clear Console Window
options(show.error.locations = TRUE); # show line numbers on error

# test

### libraries ###
library("ggplot2")      # include all GGPlot2 functions
library("tidyverse")    # plots and working with complex tables
library("RColorBrewer") # colors for graphics
library("plyr")         # sort data
library("reshape")      # sort data
library("reshape2")     # sort data
library('tmap')         # visualizing maps
library("sp")           # working with maps
library("lubridate")    # time data
library("tm")           # text mining
library("wordcloud")    # word clouds
library("gplots")       # venn diagrams
library("stringr")
library("writexl")
library("rnaturalearthdata")
library("rnaturalearth")
library("sf")
library("psych")
library('classInt')
library('devtools')
library('rnaturalearthhires')
library('rgeos')
getwd()

### Directories & Set up ###

# Root directory
#  setwd('..')           # set directory by one folder up
  dir <- paste0(getwd()); dir

# Data directory
  dat.dir <- paste0(dir,'/data/')

# Final tables
  tab.dir <- paste0(dir,'/results/')

# Final figures
  fig.dir <- paste0(dir,'/images/')

# Tables for manual edits/error checks
 dir.create(paste0(dir,'/issues/',date(Sys.Date())),recursive=TRUE)
 tab.check.dir <- paste0(dir,'/issues/',date(Sys.Date()),'/')

# custom colors
  paper_col <- c('#DDCC77','#009988','#882255')
  effect_cols <- c('#9A709E','#999999','#A50026','#FDB366','#6EA6CD')
  sigeff_col <- c("#00CC00", "#FF0000","#FF9933", "#C0C0C0")
  majeff_col <- c("#00CC00","#FF0000","#FF9933","#2274CD","#C0C0C0")

## customized theme (I just copied this from app3) ##

# my_theme = function()
# {
# theme( axis.text.y = element_text(angle = 45),
#        plot.subtitle = element_text(color ="purple", size = 11),
#        axis.text.x = element_text(face = 'italic', color = 'purple')) 
# }


```

# 3. Load data

```{r}
# surveys
  ab_screen <- read.csv(paste0(dat.dir, 'absScreening\\AbsScreen1_Merge.csv'))
  ab_maybes <- read.csv(paste0(dat.dir, 'absScreening\\AbsScreen2_maybes_to_keep.csv'))
  ab_yeses <- read.csv(paste0(dat.dir,  'absScreening\\final_sample_for_coding.csv'))
  assignments <- read.csv(paste0(dat.dir,'absScreening\\Coding_MergeAssign_R1.csv'))


  survey1 <- read.csv(paste0(dat.dir,'survey1_cleaned.csv'))
  s2 <- read.csv(paste0(dat.dir,'survey2_cleaned.csv'))
  survey3 <- read.csv(paste0(dat.dir,'survey3_cleaned.csv'))
  s23 <- read.csv(paste0(dat.dir,'s23.csv'))
# factor format
  s23$maj_eff<-factor(s23$maj_eff, c("Beneficial","Detrimental","Changed", "Mixed","Not significant or unclear"))
  s23_maj <- s23[!duplicated(s23$paper_id),]
  
```


# 4. Survey 1 & 2 Results

## 4.1 Sample Results

Accepted/rejected published papers over time

Total number of papers at the coding stage = 591

```{r}
# get total numbers but also ensure both values here match
  nrow(survey1)
  length(unique(survey1$paper_id))
```

Number of accepted and rejected papers.

Accepted = 131 (22%) , Rejected = 460 (78%)

```{r}
# get summary
  ddply(survey1, .(status), summarize,
        # total count of entries     
        count=length(status))
sum(survey1$status == 'accept')/nrow(survey1)
sum(survey1$status == 'reject')/nrow(survey1)

```

Visualizing accepted papers over time, including the ones from the abstract screening process.

```{r}
# all abstract screened papers (n=7306)
  ab_screen <- ab_screen[!ab_screen$PY==2020,] #remove 2020 studies
  ab_all <- ab_screen[!duplicated(ab_screen$TITLE),];nrow(ab_all)

# remove the papers accepted in screening from the abstract screening list (n=6665)
  ab_reject <- anti_join(ab_all,ab_maybes,by=c("TITLE"))
  ab_reject <- anti_join(ab_reject,ab_yeses,by=c("TITLE"))
  ab_reject <- ab_reject[!duplicated(ab_reject$TITLE,ab_reject$PY),];nrow(ab_reject)
    
# all papers that were accepted from abstract screening (n=641)
  ab_accept <- ab_yeses[!duplicated(ab_yeses$TITLE),]

  
# accepted papers from the assignment list for full review (n=595)
  papers_reviewed <- assignments[!duplicated(assignments$TITLE),]

# papers with PDF not available or rejected because of language (n=46)
  paper_unavail <- anti_join(ab_accept,papers_reviewed,by=c("TITLE"))
  paper_unavail <- paper_unavail[!duplicated(paper_unavail$TITLE),]
  
# rejected papers or not yet reviewed (n=460)
  
  keep <-  subset(survey1, status=='accept')
  reject <- anti_join(survey1,keep)

  papers_rejected <- anti_join(papers_reviewed,keep,by=c("STUDY_ID.1"="paper_id"))
  papers_rejected <- papers_rejected[!duplicated(papers_rejected$TITLE),]

```

```{r}
# show numbers:
  paste('original number of papers in WOS search:',nrow(ab_screen))
  paste('number of duplicates in WOS search:',nrow(ab_screen)-nrow(ab_all))
  paste('number of abstracts screened:',nrow(ab_all))
  paste('number of accepted abstracts:',nrow(ab_accept))
  paste('number of rejected abstracts:',nrow(ab_reject))
  paste('number of accepted papers unavailable or non-English:',
        nrow(paper_unavail))
  paste('number of papers available for full review:',
        nrow(papers_reviewed))
  paste('number of full papers accepted for synthesis:',
        nrow(keep)) 
  paste('number of full papers rejected from synthesis:',nrow(reject))
  paste('number of full papers not yet reviewed for synthesis:',
        nrow(papers_rejected)-nrow(reject)-5)
  
# num of full papers not yet reviewed is -1, idk why. Maybe due to common papers? The check below is True so I'm not worried.    
  
  
# test if they add up correctly
  paste('COUNT TESTS:')
  paste('total full papers:',
        nrow(papers_reviewed) == nrow(ab_accept) - nrow(paper_unavail))
  paste('total abstract screen:',
        nrow(ab_all) == nrow(ab_reject) + nrow(ab_accept))
```

Next, simplify columns and combine for three tiers in the plot.

```{r}
# select columns
  # papers found in WOS but don't meet criteria
    reject_abstract_level <- subset(ab_reject,select=c("STUDY_ID","PY"))
  # WOS papers that meet criteria but don't directly look at coupling effects on biodiv
    reject_paper_level <- subset(papers_rejected,select=c("STUDY_ID.1","PY"))
    reject_paper_level2 <- subset(paper_unavail,select=c("STUDY_ID","PY"))
  # papers that do look at coupling effects on biodiv
    accept_paper_level <- subset(keep,select=c("paper_id","year_pub"))
  
# rename columns
  colnames(reject_abstract_level) <- c('paper_id','year_pub')
  colnames(reject_paper_level) <- c('paper_id','year_pub')
  colnames(reject_paper_level2) <- c('paper_id','year_pub')
  
# add columns
  #papers that discuss tc effects on biodiv in...
  reject_abstract_level$type <- 'search but not abstract'
  reject_paper_level$type <- 'abstract but not paper'
  reject_paper_level2$type <- 'abstract but not paper'
  accept_paper_level$type <- 'abstract and paper'
  
# rbind (should be 7307 rows)
  papers <- rbind(reject_abstract_level,reject_paper_level,
                  reject_paper_level2, # <-- NOT SURE IF UNAVAILABLE PAPERS BELONG HERE
                  accept_paper_level)

# check
  nrow(papers)
```

Plot image.

```{r}
# Get a count of records per year
  paper_ct <- ddply(papers, .(year_pub,type), summarize, count=length(year_pub))

# Change to factors
  paper_ct$year_pub <- as.factor(paper_ct$year_pub)
  paper_ct$type <- factor(paper_ct$type,
                        levels = c('search but not abstract',
                                   'abstract but not paper',
                                   'abstract and paper'))
              
  papers.fig <- ggplot(paper_ct, aes(x=year_pub, y=count)) + 
                  geom_area(position="identity",
                            aes(y=count, fill = type, group = type), alpha=0.6) +
                  geom_point(aes(y =count, color = type, group = type))+
                  geom_line(aes(y =count, color = type, group = type))+
                  geom_text(aes(label=count),size=3,
                            position=position_dodge(.7),
                            vjust=-.7,
                            check_overlap=TRUE)+
                  scale_color_manual(
                  name=expression(italic("telecoupling effects\non biodiversity in...")),
                  values=paper_col)+
                  scale_fill_manual(
                  name=expression(italic("telecoupling effects\non biodiversity in...")),
                  values=paper_col)+
                  xlab("publication year")+
                  ylab("number of articles") + ylim(0,860)+
                  scale_y_continuous(breaks=seq(0,850,100)) +
                  theme_classic()+
                  theme(legend.position = c(0.22,0.87))
  
# show here
  papers.fig
```

Acceptance rate for abstract screening.

```{r}
# get total abstract acceptance rate
  sum(ab_all$INCLUDE=='YES')/nrow(ab_all)
```

Acceptance rate for papers that were reviewed (**NOTE:** this includes the 5 common surveys).

```{r}
# get total paper acceptance rate
  sum(survey1$status=='accept')/nrow(survey1)
```

Acceptance rate per person (**NOTE:** this excludes the 5 common surveys per person, but has a rate for it on its own as "all").

```{r}
# get summary
  acr <- ddply(survey1, .(coder_id), summarize,
              # total count of entries     
              count=length(coder_id),
              accept=sum(status=='accept'),
              reject=sum(status=='reject'),
              # percent acceptance
              accept_rate=sum(status=='accept')/length(coder_id))
  acr
``` 

Average per-person acceptance rates

```{r}
# mean per-person acceptance rate 
  mean(acr$accept_rate)
```


## 4.2 General Results

Counts of papers that were inferred (accepted papers only)

Total rate of **inferring** across papers.

```{r}
# get total papers for which the tc relationships were inferred
  paste('number inferred papers:',sum(keep$explicit_distant_impacts=='No'))
  paste('number explicit papers:',sum(keep$explicit_distant_impacts=='Yes'))
  
# get total inferring rate
  paste('inferred percent:',sum(keep$explicit_distant_impacts=='No')/nrow(keep))
  paste('explicit percent:',sum(keep$explicit_distant_impacts=='Yes')/nrow(keep))
```

Percent of papers inferred per person per person

```{r}
# get summary
  ddply(keep, .(coder_id), summarize,
        # total count of entries     
        count=length(coder_id),
        inferred=sum(explicit_distant_impacts=='No'),
        explicit=sum(explicit_distant_impacts=='Yes'),
        # percent inferred
        inferred_rate=sum(explicit_distant_impacts=='No')/length(coder_id))
```

Counts of study types (accepted papers only)

```{r}
# get summary
  ddply(keep, .(C4_study), summarize,
        # total count of entries     
        count=length(C4_study),
        percent=length(C4_study)/nrow(keep))
```

Habitat Frequency (study level, n= 131)

```{r}
habitat.study <- count(s2, 'habitat')
print(habitat.study)
prop.table(table(s2$habitat))

```

Taxa Frequency (study level, n=131)

```{r}
desired_length <- 8 
empty_list <- vector(mode = "list", length = desired_length)

taxa <- (s2$taxa)
table(taxa)
taxa.list <- c('Mammals', 'Plants', 'Reptiles', 'Amphibians', 'Birds', 'Fish', 'Invertebrates', 'Other')
taxa.count <- empty_list

for (i in 1:length(taxa.list)) {
  
  taxa.count[i] <- sum(str_count(taxa, taxa.list[i]))
    }

taxa.count <- rbind(taxa.list,taxa.count)
taxa.count

multiple <- str_count(taxa, ';')
multiple <- multiple != 0
multiple <- table(multiple) ["TRUE"]
multiple

# Others? Not a big deal since taxa is clarified in survey 3.Not a big deal.

othTaxa <- s2[which(s2$taxa == 'Other'),]

```

Flow frequency (study level, n=131)

```{r}
desired_length <- 10 
empty_list <- vector(mode = 'list', length = desired_length)

tc <- s2$tele_cat
tc.list <-c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer")
tc.count <- empty_list

for (i in 1:length(tc.list)) {
  
  tc.count[i] <- sum(str_count(tc, tc.list[i]))
    }

tc.count <- rbind(tc.list,tc.count)
tc.count


# Can't get loop to count the migration values for some reason, manual input code below
# Migration (human) n=4     # Migration (non-human) n=0
tc.table <- table(s2$tele_cat)

tc.count[2,4] <- tc.table[5] + tc.table[13]      # Migration (human) n=6     # Migration (non-human) n-7

tc.count

#gather(tc.count)

multiple <- str_count(tc, ';')
multiple <- multiple != 0
multiple <- table(multiple) ["TRUE"]
multiple

```

Number of metrics reported by each paper

```{r}
# get summary
  ddply(survey3, .(paper_id), summarize,
        # total count of entries     
        num_entries=length(entry_id),
        perc_dataset=length(entry_id)/nrow(survey3),
        num_taxa=length(unique(taxa))) %>% 
    arrange(desc(perc_dataset))

num.metric <- count(survey3$paper_id)
range(num.metric$freq)
sum(num.metric$freq)

```

Number of metrics by taxa and paper

```{r}
# get summary
  a <- ddply(survey3, .(taxa), summarize,
        # total count of entries     
        num_entries=length(entry_id),
        perc_dataset=length(entry_id)/nrow(survey3),
        num_papers=length(unique(paper_id)),
        perc_papers=length(unique(paper_id))/length(unique(survey3$paper_id))) %>% 
      arrange(desc(perc_dataset))

# view
  a
```

## 4.3 Biodiversity and Flow Categories by Country

Biodiversity country map

```{r}
shp <- ne_countries(scale = 50, returnclass = 'sf') %>% #st_as_sf() %>%
  select(name, iso_a3) %>% ## , economy, income_grp
  # filter(name != 'Antarctica') %>%
  # filter(name == 'France') %>%
  dplyr::mutate(
    iso_a3 = if_else(name == 'France', 'FRA', iso_a3),
    iso_a3 = if_else(name == 'Norway', 'NOR', iso_a3))
# plot(shp[1])

shp %>% filter(name == 'Norway')

### add new country name that are consistant with names uned in SDG data
# library(readxl)
# xls.shp.info <- paste0(dir, '/update_0503_SUM_dist/_input_data/ne_10m_admin_0_countries/Table/ne_10m_admin_0_countries-Export_Output.xls')
#
# nation_new_name <-
#   read_excel(path = xls.shp.info,
#              sheet = "dat", col_names = T) %>%
#   select(ADMIN, ADM0_A3, nation_name)
# names(nation_new_name)
# nation_new_name <- as.data.frame(nation_new_name[,-c(3,4)])




### theme, font --------------------------------------------------------------------------------------
font      <- 'sans' ## = "TT Arial"
font_size <- 6.5 ## max = 7; min = 5 for Nature Sustainability
map_theme <- ggpubr::theme_transparent()+
  theme(
    axis.title.x=element_blank(),
    axis.title.y=element_blank(),
    axis.text.x=element_blank(),
    axis.ticks = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    legend.position = c(0.09, 0.38),
    legend.key.size = unit(0.3, "cm"),
    # legend.key.height = unit(0.5, "cm"),
    legend.key = element_rect(fill = NA, colour = NA, size = 0.25),
    
    panel.background = element_rect(fill = "transparent", colour = NA),
    plot.background = element_rect(fill = "transparent", colour = NA),
    legend.background = element_rect(fill = "transparent", colour = NA),
    legend.box.background = element_rect(fill = "transparent", colour = NA),
    text=element_text(family=font, size=font_size))


### - Read in Data

df99 <- read.csv(paste0(dat.dir, 'survey2_cleaned.csv'))


### - list_countries
ctr_sys <- df99 %>%
  select(paper_id, list_countries) %>%
  data.frame(., do.call(rbind, str_split(.$list_countries,';'))) %>%
  gather(key = 'key', value = list_countries, 3:ncol(.)) %>%
  dplyr::mutate(list_countries = trimws(list_countries)) %>%
  dplyr::distinct(paper_id, list_countries, .keep_all = T) %>%
  filter(list_countries != '') %>%
  arrange(paper_id) %>%
  group_by(list_countries) %>%
  tally()%>%
  arrange(desc(n)) #%>%
# str(ctr_sys)


### join new name table
shp_df <- shp %>%
  left_join(., ctr_sys, by=c("iso_a3" = "list_countries"))

### check the join
shp_df_check <- merge(
  shp, ctr_sys, by.x = "iso_a3", by.y = "list_countries", all.y=T) %>%
  st_drop_geometry()

# str(shp_df)
unique(shp_df$n)


### breaks and colors
var <- shp_df$n
max <- max(var, na.rm = T); max
min <- min(var, na.rm = T); min

breaks <- seq(min, max, 2); breaks; length(breaks)
breaks <- sort(unique(shp_df$n)); breaks; length(breaks)
myPalette <- colorRampPalette((brewer.pal(8, "Greens")));# myPalette; rev
colors <- myPalette(length(breaks)); colors
title <- 'Entire system\nNumber of papers'


### - biodiv_countries
ctr_bio <- df99 %>%
  select(paper_id, biodiv_countries) %>%
  data.frame(., do.call(rbind, str_split(.$biodiv_countries,';'))) %>%
  gather(key = 'key', value = biodiv_countries, 3:ncol(.)) %>%
  dplyr::mutate(biodiv_countries = trimws(biodiv_countries)) %>%
  dplyr::distinct(paper_id, biodiv_countries, .keep_all = T) %>%
  filter(biodiv_countries != '') %>%
  arrange(paper_id) %>%
  group_by(biodiv_countries) %>%
  tally()%>%
  arrange(desc(n)) #%>%
# str(ctr_bio)


### join new name table
shp_df <- shp %>%
  left_join(., ctr_bio, by=c("iso_a3" = "biodiv_countries"))

# str(shp_df)
unique(shp_df$n)

### check the join
shp_df_check <- shp %>%
  right_join(., ctr_bio, by=c("iso_a3" = "biodiv_countries"))

### breaks and colors
var <- shp_df$n
max <- max(var, na.rm = T); max
min <- min(var, na.rm = T); min

breaks <- seq(min, max, 2); breaks; length(breaks)
breaks <- sort(unique(shp_df$n)); breaks; length(breaks)
myPalette <- colorRampPalette((brewer.pal(8, "Purples")));# myPalette; rev
colors <- myPalette(length(breaks)); colors
title <- 'Biodiversity system\nNumber of papers'

### plot
fig2 <- ggplot(data = shp_df) +
  geom_sf(aes(fill = n), color='gray50', size=0.01) +
  scale_fill_gradientn(
    name = title,
    colours= colors, na.value = "gray90",
    limits = c(min,max), breaks = breaks) +
  guides(fill = guide_legend(label.hjust = 0, label = T,
                             reverse = T, title = title))+
  map_theme
fig2
dir
fname <- paste0(fig.dir, 'Fig_map_country_bio.jpg'); fname


```

Continent distribution, study level (n=131)

```{r, results='hide'}
table(ctr_bio$biodiv_countries)

# install.packages("jsonlite", repos="https://cran.rstudio.com/")
library("jsonlite")
json_file <- 'https://datahub.io/JohnSnowLabs/country-and-continent-codes-list/datapackage.json'
json_data <- fromJSON(paste(readLines(json_file), collapse=""))
# get list of all resources:
print(json_data$resources$name)

# print all tabular data(if exists any) to 'data'
for(i in 1:length(json_data$resources$datahub$type)){
  if(json_data$resources$datahub$type[i]=='derived/csv'){
    path_to_file = json_data$resources$path[i]
    data <- read.csv(url(path_to_file))
    print(data)
  }
}

cont <- cbind(data$Continent_Name,data$Country_Name,data$Three_Letter_Country_Code)
cont <- as.data.frame(cont)

# Match continent and country name to biodiversity countries
names(cont)[1:3] <- c("continent","ctr_name","ctr_code")

ctr_bio$continent <- cont$continent[match(ctr_bio$biodiv_countries,cont$ctr_code)]  # add continent name
ctr_bio$ctr_name <- cont$ctr_name[match(ctr_bio$biodiv_countries,cont$ctr_code)]  # add country name


BUC <- aggregate(x = ctr_bio$n,
                               by = list(ctr_bio$continent),
                               FUN = sum)
zz <- ctr_bio[-which(ctr_bio$biodiv_countries == 'BRA' |
                    ctr_bio$biodiv_countries == 'USA' |
                    ctr_bio$biodiv_countries == 'CHN'),]
BUC.no <- aggregate(x = zz$n,
                               by = list(zz$continent),
                               FUN = sum)
```

heat map table of countries and flow type

```{r}

## Percentage of telecoupling

k <- as.data.frame(cbind(df99$biodiv_countries, df99$tele_cat))
colnames(k) <- c('ctr', 'tc')

ctr_ls <- ctr_bio[1]

k$ctr[k$ctr == ""] <- NA

k$tc <- as.character(k$tc)

poo <- separate_rows(k, tc, sep=";", convert = TRUE)
doo <-separate_rows(poo, ctr, sep=";", convert = TRUE)


woo <- paste0(doo$ctr, '_', doo$tc)
woot <- as.data.frame(table(woo))

ok <- str_split_fixed(woot$woo, '_', 2)
woot$ctr <- ok[,1]
woot$tc <- ok[,2]


### count by ctr and tc
booty <- doo %>%
  dplyr::select(ctr, tc) %>%
  ### how many tcs in total for each ctr?
  ungroup() %>%
  group_by(ctr) %>%
  add_tally(name = 'total_tc') %>%
  ### the number of each tc
  dplyr::ungroup() %>%
  dplyr::group_by(ctr, total_tc) %>%
  dplyr::count(tc, name = 'n_tc') %>%
  arrange(ctr) %>%
  dplyr::mutate(pct_tc = n_tc/total_tc*100)


booty_check <-  booty %>%
  dplyr::group_by(ctr) %>%
  dplyr::summarise(sum = sum(pct_tc, na.rm = T))

booty2 <- booty[order(-booty$total_tc,booty$ctr, -booty$n_tc),]

# Load data of number of studies by taxa and flow
nr_ctr <- aggregate(x = booty2$n_tc,
                               by = list(booty2$ctr,booty2$tc),
                               FUN = sum)



# Rename columns

names(nr_ctr)[1:3] <- c("ctr","tc","count")

# Fill the gaps

mat_nr_ctr <-dcast(nr_ctr, ctr ~ tc, value.var = 'count')
filled_nr_ctr <- melt(mat_nr_ctr, id=c("ctr"))
filled_nr_ctr[is.na(filled_nr_ctr)] <- 0
names(filled_nr_ctr)[2:3] <- c("tc", "count")

# Subset for countries >5 total tc

filled_nr_ctr$n_tc <- booty2$total_tc[match(filled_nr_ctr$ctr, booty2$ctr)]
filled_nr_ctr<- filled_nr_ctr[which(filled_nr_ctr$n_tc > 5),]
filled_nr_ctr<-filled_nr_ctr[order(-filled_nr_ctr$n_tc),]


# Change order of factor levels for consistency with other figures

filled_nr_ctr$ctr <- factor(filled_nr_ctr$ctr,levels=c(unique(filled_nr_ctr$ctr[order(filled_nr_ctr$n_tc)])))

filled_nr_ctr$tc <- factor(filled_nr_ctr$tc,levels=c("Energy Transfer","Investment","Knowledge Transfer",
                                                      "Migration (human)","Migration (non-human)","Species Dispersal",
                                                      "Tourism","Trade","Waste Transfer","Water Transfer"))

        
# Heatmap plot


heatmap_ctr <- ggplot(filled_nr_ctr,
                      aes(x=tc, y=ctr, fill=count)) +
                      geom_tile(color = "white", size=0.25) +
                      geom_text(aes(label = count )) +
                      labs(x="",y="")+
                      scale_y_discrete(expand=c(0,0))+
                      theme_grey(base_size=8)+
                      scale_fill_gradientn(colours = c('#FFFFFF','gray30')) +
                      theme(legend.title = element_text(size = 10),
                      legend.text = element_text(size = 10, face="bold"),
                      plot.background=element_blank(),
                      plot.title = element_blank(),
                      axis.title= element_blank(),
                      axis.ticks = element_blank(),
                      axis.text.x.top = element_text(size=10, angle = 90, vjust=0,
                                                     hjust = 0),
                      axis.text.y.left = element_text(size=10, angle = 360, vjust=0.5,
                                                      hjust = 0),
                      strip.background = element_rect(fill="white"),
                      panel.spacing = unit(0.1, "lines")) +
                      scale_x_discrete(position = "top") +
                      labs(fill = "number of entries")

heatmap_ctr

```


# 5. Telecoupling Impact by Taxa

Note that there are five papers that reported more than one taxa. The maj_effect is not accurate for those five papers currently. This will be addressed soon. 

- When studies reported significant results, the majority were significantly detrimental for biodiversity.
- Studies that quantified impacts to mammals were overwhelmingly detrimental compared to the other groups. 
- Birds and plants had more beneficial impacts, relative to the other groups.
- Amphibians were greatly underrepresented. 


```{r}
# get summary
  a <- ddply(s23_maj, .(taxa, maj_eff), summarize,
          # total count of entries     
          count=length(taxa)) %>%
          # percents of effects within totals per taxa
          group_by(taxa) %>%
            nest() %>% 
             mutate(perc_per_taxa=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_taxa))
# save as csv
#  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_taxa.csv'),row.names = TRUE)

# Stack plot (count)
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=count, x=taxa)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("")

```


```{r}
# Stack plot (percentage)
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=perc_per_taxa, x=taxa)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("")
```


# 6. Telecoupling Impact by Habitat

- Terrestrial habitats were studied the most.
- All habitats had more detrimental impacts on their respective biodiversity metrics.

```{r}
# get summary
  a <- ddply(s23_maj, .(hab, maj_eff), summarize,
          # total count of entries     
          count=length(hab)) %>%
          # percents of effects within totals per hab
          group_by(hab) %>%
            nest() %>% 
             mutate(perc_per_hab=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_hab))
# save as csv
#  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_hab.csv'), row.names = TRUE)

# Stack plot (count)
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=count, x=hab)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("")

# view
  quick_plot
```


```{r}
# Stack plot (percent)
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=perc_per_hab, x=hab)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("")
quick_plot

```

# 7. Telecoupling Impact by Flow

Duplicate rows with multiple flow types. This means that effects and other results will be *duplicated* as well.

The reason for doing this is so that we can attribute biodiversity impacts to the specific flows that may have been studied together, and whose individual impacts cannot be decoupled.

- Tourism and Trade were the most represented in our sample and both had majority detrimental imapcts reported.
- The flow categories that showed somewhat beneficial impacts where Investment, Water Transfer, and Knowledge Transfer.

```{r}

# set as character
  s23_maj$tc <- as.character(s23_maj$tc)

# show original length of rows
  print(paste('Original number of rows:',nrow(s23_maj)))

# split multiple flows listed in a row into other new rows
  tcRep_maj <- separate_rows(s23_maj, tc, sep=";", convert = TRUE)
  tcRep_maj$tc <- as.factor(tcRep_maj$tc)

# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(tcRep_maj)))

# show levels
#  summary(tcRep$tc)

# get summary
  a <- ddply(tcRep_maj, .(tc, maj_eff), summarize,
          # total count of entries     
          count=length(tc)) %>%
          # percents of effects within totals per tc
          group_by(tc) %>%
            nest() %>% 
             mutate(perc_per_tc=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_tc))
# save as csv
#  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_flow.csv'),row.names = TRUE)
  
# Stack plot (count)
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=count, x=tc)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("")


# view
  quick_plot
```

```{r}
# Stack plot (percent)
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=perc_per_tc, x=tc)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                scale_fill_manual(values=majeff_col) +
                xlab("")

quick_plot
```


# 8. Telecoupling impacts by metric type and flow

Replicate TC flows by entry

- This figure shows the direction of telecoupling impacts at the entry level (i.e. all 700+ metrics recorded)
- Most studies report multiple species richness and abundance. 
- Most habitat metrics were significantly detrimental, except in the case of knowledge transfer telecouplings.

```{r}
# set as character
  s23$tc <- as.character(s23$tc)
  poo<-s23[is.na(s23$tc),]
  
  
# show original length of rows
  print(paste('Original number of rows:',nrow(s23)))

# split multiple flows listed in a row into other new rows
  tcRep <- separate_rows(s23, tc, sep=";", convert = TRUE)
  tcRep$tc <- as.factor(tcRep$tc)

# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(tcRep)))
  
  tcRep_maj <- tcRep[!duplicated(tcRep$paper_id),]


```

Convert to long format, where metric is indicated.

```{r}
# subset
  metrics <- subset(tcRep,
                    select=c('paper_id','entry_id',
                            'taxa','tc','sig_effect',
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  metrics_long <- melt(metrics, id.vars=c('paper_id','entry_id',
                            'taxa','tc','sig_effect'))
  
# remove NA fields
  metrics_long <- metrics_long[!is.na(metrics_long$value),]

# change colnames
  colnames(metrics_long)[6] <- 'metric_type'
  colnames(metrics_long)[7] <- 'metric'


# change levels
  levels(metrics_long$metric_type) <- c('Single species',
                                        'Multiple species',
                                        'Habitat')

  levels(as.factor(metrics_long$metric))

# remove parentheses
  metrics_long$metric <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metrics_long$metric))

# capitalize each word
  metrics_long$metric <- tools::toTitleCase(metrics_long$metric)
  
# adjust name
  metrics_long$metric <- gsub("With-in", 'Within',
                        as.character(metrics_long$metric))
  
# change levels, moving other to the end
  metrics_long$metric <- factor(metrics_long$metric,
                                c("Abundance/Density",
                                   "Amount",
                                   "Composition",
                                   "Detection",
                                   "Diversity Index",
                                   "Evenness",
                                   "Movement",
                                   "Occurrence",
                                   "Population Dynamics",
                                   "Quality",
                                   "Richness",
                                   "Within Species Diversity"
                                  ))
  
# check levels
  levels(as.factor(metrics_long$metric))

# get summary
  metric_flow <- ddply(metrics_long,
                       .(metric_type, metric, tc, sig_effect),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
#  write.csv(metric_flow, paste0(tab.dir,'synthesis_sig_effects_metric_and_flow.csv'),row.names = TRUE)

# sig_effects level change
  metric_flow$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metric_flow$sig_effect))
  metric_flow$sig_effect <- factor(metric_flow$sig_effect,
                             c( "Beneficial","Detrimental","Changed","Not significant or unclear"))
# telecoupling level change
  metric_flow$tc <- factor(metric_flow$tc,
                                c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
  
```

Figure code

```{r}
# Matrix of pie charts
  sig_effect_cols <- sigeff_col

  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity',
                             width = 1,
                             size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric_type ~ metric ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=8)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                


# display image
  metric_flow_fig
```

Heatmap

```{r}
# Load data of number of studies by taxa and flow
nr_metric_tele <- aggregate(x = metric_flow$count,
                               by = list(metric_flow$metric_type,metric_flow$metric, metric_flow$tc),
                               FUN = sum)

 

# Rename columns

names(nr_metric_tele)[1:4] <- c("type","metric", "telecoupling", "count")

nr_metric_tele$metricType <- paste(nr_metric_tele$type,nr_metric_tele$metric)   

# Fill the gaps

mat_nr_metric_tele <-dcast(nr_metric_tele, metricType ~ telecoupling, value.var = 'count')
filled_nr_metric_tele <- melt(mat_nr_metric_tele, id=c("metricType"))
filled_nr_metric_tele[is.na(filled_nr_metric_tele)] <- 0
names(filled_nr_metric_tele)[2:3] <- c("telecoupling", "count")

# Create 'count' categories for representation

filled_nr_metric_tele$count_factor <- cut(filled_nr_metric_tele$count,
                                          breaks = c(-1,0,5,10,20,50,100,max(filled_nr_metric_tele$count,na.rm=T)),
                                          labels=c("0","1-5","5-10","10-20","20-50","50-100",">100"))


# Change order of factor levels for consistency with other figures

filled_nr_metric_tele$metricType <- as.character(filled_nr_metric_tele$metricType)

filled_nr_metric_tele$metricType <- factor(filled_nr_metric_tele$metricType,
          levels=c("Habitat Quality",
                   "Habitat Amount",
                   "Multiple species Richness",
                   "Multiple species Population Dynamics",
                   "Multiple species Occurrence",
                   "Multiple species Evenness",
                   "Multiple species Diversity Index",
                   "Multiple species Composition",
                   "Multiple species Abundance/Density",
                   "Single species Within Species Diversity",
                   "Single species Population Dynamics",
                   "Single species Occurrence",
                   "Single species Movement",
                   "Single species Abundance/Density"
          ))
# Heatmap plot

heatmap_telemetric <- ggplot(filled_nr_metric_tele,
                      aes(x=telecoupling, y=metricType, fill=count_factor)) +
                      geom_tile(color = "white", size=0.25) +
                    geom_text(aes(label = count )) +
 scale_fill_manual(values=c("grey90","#BCDDF5","#8FCBF5","#4EA6E6",
                                               "#4E91CC","#3F76A6","#274866"))+
                      labs(x="",y="")+
                      scale_y_discrete(expand=c(0,0))+
                      theme_grey(base_size=8)+

                      theme(legend.title = element_text(size = 10),
                      legend.text = element_text(size = 10, face="bold"),
                      plot.background=element_blank(),
                      plot.title = element_blank(),
                      axis.title= element_blank(),
                      axis.ticks = element_blank(),
                      axis.text.x.top = element_text(size=10, angle = 90, vjust=0,
                                                     hjust = 0),
                      axis.text.y.left = element_text(size=10, angle = 360, vjust=0.5,
                                                      hjust = 0),
                      strip.background = element_rect(fill="white"),
                      panel.spacing = unit(0.1, "lines")) +
                      scale_x_discrete(position = "top") +
                      labs(fill = "number of entries")

heatmap_telemetric

                   

                    
                    

```




