---
title: 'MCBD: Synthesis of Metacoupled Effects on Biodiversity'
author: "Ciara Hovis, CSIS Lab, Michigan State University"
date: "September 16, 2020"
output: 
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: true
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Methods summary

Synthesis of survey 2 and 3 results for metacoupling/biodiversity systematic review. It consists of response summaries and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.2; R Core Team 2020) and its packages.

Load libraries, directories, and custom functions from source file.

```{r}
# Source file
rm(list=ls())               
getwd()
  source('./scripts/Reference.R')
```

# 3. Load data

```{r}
# surveys
  ab_screen <- read.csv(paste0(dat.dir, 'absScreening\\AbsScreen1_Merge.csv'))
  ab_maybes <- read.csv(paste0(dat.dir, 'absScreening\\AbsScreen2_maybes_to_keep.csv'))
  ab_yeses <- read.csv(paste0(dat.dir,  'absScreening\\final_sample_for_coding.csv'))
  assignments <- read.csv(paste0(dat.dir,'absScreening\\Coding_MergeAssign_R1.csv'))


  survey1 <- read.csv(paste0(dat.dir,'survey1_cleaned.csv'))
  s2 <- read.csv(paste0(dat.dir,'survey2_cleaned.csv'))
  survey3 <- read.csv(paste0(dat.dir,'survey3_cleaned.csv'))
  s23 <- read.csv(paste0(dat.dir,'s23.csv'))
  
```

Show column names

```{r}
# get col names
  colnames(s23)
```


# 4. Survey 1 Summary

## 4.1 Accepted/rejected published papers over time

Total number of papers = 591

```{r}
# get total numbers but also ensure both values here match
  nrow(survey1)
  length(unique(survey1$paper_id))
```

Number of accepted and rejected papers.

Accepted = 135 (23%) , Rejected = 456 (77%)

```{r}
# get summary
  ddply(survey1, .(status), summarize,
        # total count of entries     
        count=length(status))
sum(survey1$status == 'accept')/nrow(survey1)
sum(survey1$status == 'reject')/nrow(survey1)

```

### 4.1.1 Visualizing accepted papers over time

Visualizing accepted papers over time, including the ones from the abstract screening process.

```{r}
# all abstract screened papers (n=7306)
  ab_screen <- ab_screen[!ab_screen$PY==2020,] #remove 2020 studies
  ab_all <- ab_screen[!duplicated(ab_screen$TITLE),]

# remove the papers accepted in screening from the abstract screening list (n=6665)
  ab_reject <- anti_join(ab_all,ab_maybes,by=c("TITLE"))
  ab_reject <- anti_join(ab_reject,ab_yeses,by=c("TITLE"))
  ab_reject <- ab_reject[!duplicated(ab_reject$TITLE,ab_reject$PY),]
    
# all papers that were accepted from abstract screening (n=641)
  ab_accept <- ab_yeses[!duplicated(ab_yeses$TITLE),]

  
# accepted papers from the assignment list for full review (n=595)
  papers_reviewed <- assignments[!duplicated(assignments$TITLE),]

# papers with PDF not available or rejected because of language (n=46)
  paper_unavail <- anti_join(ab_accept,papers_reviewed,by=c("TITLE"))
  paper_unavail <- paper_unavail[!duplicated(paper_unavail$TITLE),]
  
# rejected papers or not yet reviewed (n=460)
# number does not match up with the reject number (456), could be due to study_id's changing during cleaning
  keep <-  subset(survey1, status=='accept')
  reject <- anti_join(survey1,keep)

  papers_rejected <- anti_join(papers_reviewed,keep,by=c("STUDY_ID.1"="paper_id"))
  papers_rejected <- papers_rejected[!duplicated(papers_rejected$TITLE),]
  
# show numbers:
  paste('original number of papers in WOS search:',nrow(ab_screen))
  paste('number of duplicates in WOS search:',nrow(ab_screen)-nrow(ab_all))
  paste('number of abstracts screened:',nrow(ab_all))
  paste('number of accepted abstracts:',nrow(ab_accept))
  paste('number of rejected abstracts:',nrow(ab_reject))
  paste('number of accepted papers unavailable or non-English:',
        nrow(paper_unavail))
  paste('number of papers available for full review:',
        nrow(papers_reviewed))
  paste('number of full papers accepted for synthesis:',
        nrow(keep)) #REMEMBER YOU NEED THE 5 COMMON PAPERS
  paste('number of full papers rejected from synthesis:',nrow(reject))
  paste('number of full papers not yet reviewed for synthesis:',
        nrow(papers_rejected)-nrow(reject)-5) #THE 5 COMMON PAPERS NOT IN DATASET YET
  
# test if they add up correctly
  paste('COUNT TESTS:')
  paste('total full papers:',
        nrow(papers_reviewed) == nrow(ab_accept) - nrow(paper_unavail))
  paste('total abstract screen:',
        nrow(ab_all) == nrow(ab_reject) + nrow(ab_accept))
```

Next, simplify columns and combine for three tiers in the plot.

```{r}
# select columns
  # papers found in WOS but don't meet criteria
    reject_abstract_level <- subset(ab_reject,select=c("STUDY_ID","PY"))
  # WOS papers that meet criteria but don't directly look at coupling effects on biodiv
    reject_paper_level <- subset(papers_rejected,select=c("STUDY_ID.1","PY"))
    reject_paper_level2 <- subset(paper_unavail,select=c("STUDY_ID","PY"))
  # papers that do look at coupling effects on biodiv
    accept_paper_level <- subset(keep,select=c("paper_id","year_pub"))
  
# rename columns
  colnames(reject_abstract_level) <- c('paper_id','year_pub')
  colnames(reject_paper_level) <- c('paper_id','year_pub')
  colnames(reject_paper_level2) <- c('paper_id','year_pub')
  
# add columns
  #papers that discuss tc effects on biodiv in...
  reject_abstract_level$type <- 'search but not abstract'
  reject_paper_level$type <- 'abstract but not paper'
  reject_paper_level2$type <- 'abstract but not paper'
  accept_paper_level$type <- 'abstract and paper'
  
# rbind (should be 7307 rows)
  papers <- rbind(reject_abstract_level,reject_paper_level,
                  reject_paper_level2, # <-- NOT SURE IF UNAVAILABLE PAPERS BELONG HERE
                  accept_paper_level)
  
# check
  nrow(papers)
```

Plot image.

```{r, fig.width=5,fig.height=5}
# Get a count of records per year
  paper_ct <- ddply(papers, .(year_pub,type), summarize, count=length(year_pub))

# Change to factors
  paper_ct$year_pub <- as.factor(paper_ct$year_pub)
  paper_ct$type <- factor(paper_ct$type,
                        levels = c('search but not abstract',
                                   'abstract but not paper',
                                   'abstract and paper'))
              
  papers.fig <- ggplot(paper_ct, aes(x=year_pub, y=count)) + 
                  geom_area(position="identity",
                            aes(y=count, fill = type, group = type), alpha=0.6) +
                  geom_point(aes(y =count, color = type, group = type))+
                  geom_line(aes(y =count, color = type, group = type))+
                  geom_text(aes(label=count),size=3,
                            position=position_dodge(.7),
                            vjust=-.7,
                            check_overlap=TRUE)+
                  scale_color_manual(
                  name=expression(italic("telecoupling effects\non biodiversity in...")),
                  values=paper_col)+
                  scale_fill_manual(
                  name=expression(italic("telecoupling effects\non biodiversity in...")),
                  values=paper_col)+
                  xlab("publication year")+
                  ylab("number of articles") + ylim(0,860)+
                  scale_y_continuous(breaks=seq(0,850,100)) +
                  theme_classic()+
                  theme(legend.position = c(0.22,0.87))
  
# save image
  ggsave(filename=paste0(fig.dir,"Figure_2_papers_over_time.png"),
         plot=papers.fig, height = 5, width = 5)

# show here
  papers.fig
```

### 4.1.2 Acceptance rate at each level of review

Acceptance rate for abstract screening.

```{r}
# get total abstract acceptance rate
  sum(ab_all$INCLUDE=='YES')/nrow(ab_all)
```

Acceptance rate for papers that were reviewed (**NOTE:** this includes the 5 common surveys).

```{r}
# get total paper acceptance rate
  sum(survey1$status=='accept')/nrow(survey1)
```

Acceptance rate per person (**NOTE:** this excludes the 5 common surveys per person, but has a rate for it on its own as "all").

```{r}
# get summary
  acr <- ddply(survey1, .(coder_id), summarize,
              # total count of entries     
              count=length(coder_id),
              accept=sum(status=='accept'),
              reject=sum(status=='reject'),
              # percent acceptance
              accept_rate=sum(status=='accept')/length(coder_id))
  acr
``` 

Average per-person acceptance rates

```{r}
# mean per-person acceptance rate 
  mean(acr$accept_rate)
```


## 4.3 Counts of study types (accepted papers only)

```{r}
# get summary
  ddply(keep, .(C4_study), summarize,
        # total count of entries     
        count=length(C4_study),
        percent=length(C4_study)/nrow(keep))
```

## 4.4 Counts of papers that were inferred (accepted papers only)

Total rate of **inferring** across papers.

```{r}
# get total papers for which the tc relationships were inferred
  paste('number inferred papers:',sum(keep$explicit_distant_impacts=='No'))
  paste('number explicit papers:',sum(keep$explicit_distant_impacts=='Yes'))
  
# get total inferring rate
  paste('inferred percent:',sum(keep$explicit_distant_impacts=='No')/nrow(keep))
  paste('explicit percent:',sum(keep$explicit_distant_impacts=='Yes')/nrow(keep))
```

Percent of papers inferred per person per person

```{r}
# get summary
  ddply(keep, .(coder_id), summarize,
        # total count of entries     
        count=length(coder_id),
        inferred=sum(explicit_distant_impacts=='No'),
        explicit=sum(explicit_distant_impacts=='Yes'),
        # percent inferred
        inferred_rate=sum(explicit_distant_impacts=='No')/length(coder_id))
```


# 5. Survey 2 & 3 Summary

## 5.1 Habitat Frequency 

By study

```{r}
# By study 

habitat.study <- count(s2, 'habitat')
print(habitat.study)
prop.table(table(s2$habitat))

p<-ggplot(data=habitat.study, aes(x=habitat, y=freq)) +
  geom_bar(stat="identity")
p

# By entry (REPLICATED FLOW ID NOT RMVD YET)

habitat.entry <- count(s23, 'hab')
print(habitat.entry)
prop.table(table(s23$habitat))


```


## 5.2 Taxa Frequency 


```{r}
# By study 
desired_length <- 8 
empty_list <- vector(mode = "list", length = desired_length)

taxa <- (s2$taxa)
taxa.list <- c('Mammals', 'Plants', 'Reptiles', 'Amphibians', 'Birds', 'Fish', 'Invertebrates', 'Other')
taxa.count <- empty_list

for (i in 1:length(taxa.list)) {
  
  taxa.count[i] <- sum(str_count(taxa, taxa.list[i]))
    }

taxa.count <- rbind(taxa.list,taxa.count)
taxa.count

multiple <- str_count(taxa, ';')
multiple <- multiple != 0
multiple <- table(multiple) ["TRUE"]


# By entry 

taxa.entry <- count(s23, 'taxa')
print(taxa.entry)
prop.table(table(s23$taxa))


```

## 5.3 Telecoupling Flow Category Frequency

```{r}
count(s2$tele_cat)

count(s23$tele_cat)

```

## 5.4 Number of entries per paper

Get number of papers and percent of the dataset each paper covers. This can give an idea on the weight of the papers on our results.

```{r}
# get summary
  ddply(survey3, .(paper_id), summarize,
        # total count of entries     
        num_entries=length(entry_id),
        perc_dataset=length(entry_id)/nrow(survey3),
        num_taxa=length(unique(taxa))) %>% 
    arrange(desc(perc_dataset))
```

## 5.5 Summary of taxa across papers

```{r}
# get summary
  a <- ddply(survey3, .(taxa), summarize,
        # total count of entries     
        num_entries=length(entry_id),
        perc_dataset=length(entry_id)/nrow(survey3),
        num_papers=length(unique(paper_id)),
        perc_papers=length(unique(paper_id))/length(unique(survey3$paper_id))) %>% 
      arrange(desc(perc_dataset))

# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_number_taxa.csv'),
            row.names = TRUE)
  
# view
  a
```

## 5.6 Summary of biodiversity metrics

```{r}
# get summary
  a <- ddply(survey3, .(taxa), summarize,
          # total count of entries     
          num_taxonomic=sum(taxon_or_func=='Taxonomic'),
          perc_taxonomic=sum(taxon_or_func=='Taxonomic')/nrow(survey3),
          num_functional=sum(taxon_or_func=='Functional'),
          perc_functional=sum(taxon_or_func=='Functional')/nrow(survey3),
          num_1sp=sum(!is.na(biodiv_cat_1sp)),
          perc_1sp=sum(!is.na(biodiv_cat_1sp))/nrow(survey3),
          num_multsp=sum(!is.na(biodiv_cat_multsp)),
          perc_multsp=sum(!is.na(biodiv_cat_multsp))/nrow(survey3),
          num_hab=sum(!is.na(biodiv_cat_habitat)),
          perc_hab=sum(!is.na(biodiv_cat_habitat))/nrow(survey3))

# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_biodiv_metrics.csv'),
            row.names = TRUE)
  
# view
  a
```

## 5.7 Summary of effects and their significance 

```{r}
# get summary
  a <- ddply(survey3, .(effect, significant), summarize,
          # total count of entries     
          count=length(effect))

# Stack plot
  quick_plot <- ggplot(a, aes(fill=effect, y=count, x=significant)) + 
                geom_bar(position="stack", stat="identity") +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                theme_classic() +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_significant_effects.png"),
         plot=quick_plot, height = 6, width = 11)
  
# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_significant.csv'),
            row.names = TRUE)
  
# view
  a
```

# 6 Summary of effects/significance

Subset s23 data for majority effects

```{r}
s23_maj <- s23[!duplicated(s23$paper_id),]
```

## 6.1 Taxa By Entry

```{r}
# get summary
  a <- ddply(s23, .(taxa, sig_effect), summarize,
          # total count of entries     
          count=length(taxa)) %>%
          # percents of effects within totals per taxa
          group_by(taxa) %>%
            nest() %>% 
             mutate(perc_per_taxa=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_taxa))
# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_taxa.csv'),
            row.names = TRUE)

# view
  a
```

Quick data visualization

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=sig_effect, y=perc_per_taxa, x=taxa)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_taxa.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```

Numbers instead of percents

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=sig_effect, y=count, x=taxa)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_taxa2.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```

### 6.2 Taxa By Study (majority effect)

```{r}
# get summary
  a <- ddply(s23_maj, .(taxa, maj_eff), summarize,
          # total count of entries     
          count=length(taxa)) %>%
          # percents of effects within totals per taxa
          group_by(taxa) %>%
            nest() %>% 
             mutate(perc_per_taxa=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_taxa))
# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_taxa.csv'),
            row.names = TRUE)

# view
  a
```

Quick data visualization

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=perc_per_taxa, x=taxa)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_taxa.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```

Numbers instead of percents

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=count, x=taxa)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_taxa2.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```


### 6.3 Habitat By Entry 

```{r}
# get summary
  a <- ddply(s23, .(hab, sig_effect), summarize,
          # total count of entries     
          count=length(hab)) %>%
          # percents of effects within totals per hab
          group_by(hab) %>%
            nest() %>% 
             mutate(perc_per_hab=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_hab))
# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_hab.csv'),
            row.names = TRUE)

# view
  a
```

Quick data visualization

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=sig_effect, y=perc_per_hab, x=hab)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_taxa.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```
Numbers instead of percents

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=sig_effect, y=count, x=hab)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_hab2.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```


### 6.4 Habitat By Study (majority effect)

```{r}
# get summary
  a <- ddply(s23_maj, .(hab, maj_eff), summarize,
          # total count of entries     
          count=length(hab)) %>%
          # percents of effects within totals per hab
          group_by(hab) %>%
            nest() %>% 
             mutate(perc_per_hab=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_hab))
# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_hab.csv'),
            row.names = TRUE)

# view
  a
```

Quick data visualization

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=perc_per_hab, x=hab)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_taxa.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```
Numbers instead of percents

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=count, x=hab)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_hab2.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```

### 6.5 Flow By Entry 

Repeat flows
**IMPORTANT STEP HERE:** 

Duplicate rows with multiple flow types. This means that effects and other results will be *duplicated* as well!!!!!!!!!!!!!!!!!!!!!!!!! 

The reason for doing this is so that we can attribute biodiversity impacts to the specific flows that may have been studied together, and whose individual impacts cannot be decoupled.
```{r}
# set as character
  s23$tele_cat <- as.character(s23$tele_cat)
  table(s23$tele_cat)
  
# show original length of rows
  print(paste('Original number of rows:',nrow(s23)))

# split multiple flows listed in a row into other new rows
  tcRep <- separate_rows(s23, tele_cat, sep=";", convert = TRUE)
  tcRep$tele_cat <- as.factor(tcRep$tele_cat)

# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(tcRep)))

# show levels
  summary(tcRep$tele_cat)
  
```

Some NA's (not sure why)

```{r}
# get summary
  a <- ddply(tcRep, .(tele_cat, sig_effect), summarize,
          # total count of entries     
          count=length(tele_cat)) %>%
          # percents of effects within totals per tele_cat
          group_by(tele_cat) %>%
            nest() %>% 
             mutate(perc_per_tele_cat=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_tele_cat))
# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_flow.csv'),
            row.names = TRUE)

# view
  a
```

Quick data visualization

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=sig_effect, y=perc_per_tele_cat, x=tele_cat)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_flow.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```

Numbers instead of percents

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=sig_effect, y=count, x=tele_cat)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_hab2.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```


### 6.6 Flow By Study (majority effect)

```{r}

# set as character
  s23_maj$tele_cat <- as.character(s23_maj$tele_cat)

# show original length of rows
  print(paste('Original number of rows:',nrow(s23_maj)))

# split multiple flows listed in a row into other new rows
  tcRep_maj <- separate_rows(s23_maj, tele_cat, sep=";", convert = TRUE)
  tcRep_maj$tele_cat <- as.factor(tcRep_maj$tele_cat)

# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(tcRep_maj)))

# show levels
  summary(tcRep$tele_cat)

# get summary
  a <- ddply(tcRep_maj, .(tele_cat, maj_eff), summarize,
          # total count of entries     
          count=length(tele_cat)) %>%
          # percents of effects within totals per tele_cat
          group_by(tele_cat) %>%
            nest() %>% 
             mutate(perc_per_tele_cat=map(data, function(x) x$count/sum(x$count))) %>% 
              unnest(cols = c(data, perc_per_tele_cat))
# save as csv
  write.csv(a, paste0(tab.dir,'survey3_summary_effects_by_flow.csv'),
            row.names = TRUE)

# view
  a
```

Quick data visualization

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=perc_per_tele_cat, x=tele_cat)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_flow.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```


Numbers instead of percents

```{r, fig.height = 6, fig.width = 11}
# Stack plot
  quick_plot <- ggplot(a, aes(fill=maj_eff, y=count, x=tele_cat)) + 
                geom_bar(position="stack", stat="identity") +
                theme_classic() +
                theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
                xlab("")

# save image
  ggsave(filename=paste0(fig.dir,"Figure_Xtra_effects_by_flow2.png"),
         plot=quick_plot, height = 6, width = 11)
  
# view
  quick_plot
```







