---
title: 'MCBD: Synthesis of Metacoupled Effects on Biodiversity'
author: "Veronica F. Frans, CSIS Lab, Michigan State University"
date: "May 30, 2020 (Updated: June 29, 2020)"
output: 
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Methods summary

Synthesis of survey 3 results for metacoupling/biodiversity systematic review. It consists of error checks, response summaries, and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.0; R Core Team 2019) and its packages.

## 2.1 Libraries

Call all libraries that you use here instead of immediately before your code chunks.

```{r,results='hide',warning=FALSE,message=FALSE}    
# libraries
  library("tidyverse")    # plots and working with complex tables
  library("RColorBrewer") # colors for graphics
  library("plyr")         # sort data
  library("reshape")      # sort data
  library("reshape2")     # sort data
  library('tmap')         # visualizing maps
  library("sp")           # working with maps
  library("lubridate")    # time data
  library("tm")           # text mining
  library("wordcloud")    # word clouds
``` 

## 2.2 Directories

We create and use multiple folders to organize our inputs and outputs. Similar directories can be made anywhere by only changing the root directory object, `dir`. 

```{r, warning=FALSE,results='hide'}
# Root directory
  dir <- paste0(getwd())

# Data directory
  dat.dir <- paste0(dir,'\\data\\cleaned_surveys\\')
  
# Final tables
  tab.dir <- paste0(dir,'\\tables\\')
  
# Final figures
  fig.dir <- paste0(dir,'\\figures\\')
```

## 2.3 Custom Functions

```{r}
## Any custom functions made/used can be stored here and then called below
```

## 2.4 Custom Colors

```{r}
# paper types
  paper_cols <- c('#DDCC77','#009988','#882255')

# effect types
  effect_cols <- c('#9A709E','#999999','#A50026','#FDB366','#6EA6CD')
```

# 3. Load data

```{r}
# load previous workspace (if needed)
  #load("synthesisResults.RData")

# surveys
  survey2 <- read.csv(paste0(dat.dir,'survey2_cleaned_20200623.csv'))
  survey3 <- read.csv(paste0(dat.dir,'survey3_cleaned.csv'))
```

# 4. Data formatting

## 4.1 Merge tables

Merge tables. The expected length of this merge should be the same as survey 3, with fields from survey 2 repeated across entries for each paper id. 

```{r}
# left join survey 2 to survey 3
  s23 <- left_join(survey3,survey2,by=c("paper_id","coder_id"))
```

Show column names

```{r}
# get col names
  colnames(s23)
```

Drop columns.

```{r}
unwanted <- c(# survey 3 fields
              'timestamp.x','notes','taxa.x',
              # survey 2 fields
              'coder_id','entry','final_decision','X',
              'taxa.y', 'timestamp.y', 'year_pub', 'author',
              'taxa_list', 'num_time_pd', 'year_start',
              'year_end','temp_res','temp_res_unk',
              'b4_dur_after','comments','further_discuss'
              )

s23$taxa <- s23$taxa.x
s23$sig_effect <- '' #adding column now because there are errors below

s23 <- s23 %>%
        select(-one_of(unwanted))
```

## 4.2 Quick cleanup of levels

Next, show levels of couplings

```{r}
levels(as.factor(s23$tele_cat))
```

```{r, echo=FALSE, eval=FALSE}
# # set as character
#   s23$tele_cat <- as.character(s23$tele_cat)
# 
# # relating to energy transfer
#   s23$tele_cat <- gsub('Chernobyl Nuclear Power Plant',
#                        'Energy Transfer',s23$tele_cat)
# 
# # relating to grazing
#   s23$tele_cat <- gsub(' and grazing/browsing',
#                        ', grazing', s23$tele_cat)
#   s23$tele_cat <- gsub('grazing',
#                        'Grazing',s23$tele_cat)
# 
# # relating to agriculture
# 
# 
# # relating to trade #####<---- or is this governance???
#   s23$tele_cat <- gsub(", Agricultural policy \\(trade inferred\\)",
#                        '',s23$tele_cat)
# 
# # relating to human consumption
#   s23$tele_cat <- gsub(', unsure, it was the intentional introduction of a fish to a lake by miners presumably',
#                        ', Human Consumption',s23$tele_cat)
#   s23$tele_cat <- gsub('unmanaged harvests for the aquarium trade',
#                        'Human Consumption',s23$tele_cat)
#   s23$tele_cat <- gsub(' \\(direct, agriculture/land use change\\)',
#                        '',s23$tele_cat)
#   s23$tele_cat <- gsub('land use',
#                        'Human Consumption',s23$tele_cat)
#   s23$tele_cat <- gsub('Cutting',
#                        'Human Consumption',s23$tele_cat)
#   s23$tele_cat <- gsub('human consumption',
#                        'Human Consumption',s23$tele_cat)
#   s23$tele_cat <- gsub('Human Consumption ',
#                        'Human Consumption',s23$tele_cat)
# 
# # relating to water transfer ####<----- or is this governance????
#   s23$tele_cat <- gsub('Water flow \\(hydrological regulation\\)',
#                        'Water Transfer',s23$tele_cat)
#   
# # relating to water transfer
#   s23$tele_cat <- gsub('nonhuman',
#                        '(non-human)',s23$tele_cat)
#   
# # relating to governance ####<----- include governance????
#   s23$tele_cat <- gsub('Agricultural policy \\(trade inferred\\)',
#                        'Governance',s23$tele_cat)
#   # s23$tele_cat <- gsub('Water flow \\(hydrological regulation\\)',
#   #                      'Governance',s23$tele_cat)
#   s23$tele_cat <- gsub('governance',
#                        'Governance',s23$tele_cat)
#   s23$tele_cat <- gsub('Governing of trade',
#                        'Governance',s23$tele_cat)
  


# Check factors again

# # set as character
#   s23$tele_cat <- as.character(s23$tele_cat)
# 
# # check levels
#   levels(as.factor(s23$tele_cat))
```

**IMPORTANT STEP HERE:** 

Duplicate rows with multiple flow types. This means that effects and other results will be *duplicated* as well!!!!!!!!!!!!!!!!!!!!!!!!!

```{r}
# set as character
  s23$tele_cat <- as.character(s23$tele_cat)

# show original length of rows
  print(paste('Original number of rows:',nrow(s23)))

# split multiple flows listed in a row into other new rows
  s23 <- separate_rows(s23, tele_cat, sep=";", convert = TRUE)
  s23$tele_cat <- as.factor(s23$tele_cat)
  
# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(s23)))

# show levels
  summary(s23$tele_cat)
```

Some have NA's. Let's see which ones they are.

```{r}
s23[is.na(s23$tele_cat),]
```

These are the **common survey** responses from Survey 2. This needs to be addressed by the Survey 2 sub-team.

# 5. First synthesis: Effects of coupling categories across taxa 

## 5.1 Summary regardless of significance

Make a new table.

```{r}
# get summary
  taxa_flow <- ddply(s23, .(taxa, tele_cat, effect), summarize,
                # total count of entries     
                count=length(taxa)) %>%
                # percents of effects within totals per taxa
                group_by(taxa) %>%
                  nest() %>% 
                   mutate(perc_per_taxa=map(data, function(x) x$count/sum(x$count))) %>%
                    unnest()

# save as csv
  write.csv(taxa_flow, paste0(tab.dir,'synthesis_effects_taxa_and_flow.csv'),
            row.names = TRUE)

# view
  taxa_flow
```

Check levels

```{r}
levels(as.factor(taxa_flow$taxa))
```

Check levels

```{r}
levels(as.factor(taxa_flow$effect))
```
```{r}
levels(as.factor(taxa_flow$tele_cat))
```

Adjust levels

```{r}
# taxa level change
  taxa_flow$taxa <- factor(taxa_flow$taxa,
                           c('Birds','Mammals','Reptiles','Amphibians',
                             'Fish','Invertebrates','Plants/trees/shrubs',
                             'Multiple'))

# effects level change
  taxa_flow$effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(taxa_flow$effect))
  taxa_flow$effect <- factor(taxa_flow$effect,
                             c('Positive','Neutral','Negative','Changed','Unclear'))

# telecoupling level change
  taxa_flow$tele_cat <- factor(taxa_flow$tele_cat,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Technology Transfer",
                                 "Tourism","Trade","Waste Transfer","Water Transfer",
                                 "Other","remove"))
```
Energy Transfer            Investment    Knowledge Transfer 
                   63                    11                    73 
    Migration (human) Migration (non-human)                 Other 
                   16                    13                    10 
               remove     Species Dispersal   Technology Transfer 
                   15                    54                     1 
              Tourism                 Trade        Waste Transfer 
                  213                   286                     2 
       Water Transfer                  NA's 
                   12                    38 
Visualize as a matrix of pie charts

```{r}
# change colors
  #effect_cols <- c('#4EB265','#999999','#A50026','#FDB366','#9A709E')
  effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  
# Matrix of pie charts
  taxa_flow_fig <- ggplot(taxa_flow) + 
                    aes(x='', y = count, fill = effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(taxa ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ taxa, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y = element_text(size=10,
                                          angle=180, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('') 
                
# save image
  ggsave(taxa_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_effects_taxa_and_flow_Vert.png'),
                         'synthesis_effects_taxa_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  taxa_flow_fig
```

## 5.2 Summary emphasizing significance

Make a new column for significant effects; non-significant becomes a new level in this dataset.

```{r}
# new column of significant effects; non-significant effects renamed
  s23$sig_effect <- ''
  s23$sig_effect <- as.character(s23$significant)
  s23$effect <- as.character(s23$effect)
  s23$sig_effect[is.na(s23$sig_effect)] <- "Unknown Signif."
  s23$sig_effect[s23$sig_effect=='Not evaluated'] <- "Unknown Signif."
  s23$sig_effect[s23$sig_effect=='FALSE'] <- "Not Signif."
  s23$sig_effect[s23$sig_effect=='TRUE'] <- s23$effect[s23$sig_effect=='TRUE']
```

Summarize new column by taxa and telecoupling category.

```{r}
# get summary
  taxa_flow_sig <- ddply(s23, .(taxa, tele_cat, sig_effect), summarize,
                        # total count of entries     
                        count=length(taxa))
# save as csv
  write.csv(taxa_flow_sig,
            paste0(tab.dir,'synthesis_effects_taxa_and_flow_significant.csv'),
            row.names = TRUE)

# view
  taxa_flow_sig
```

Change levels

```{r}
# taxa level change
  taxa_flow_sig$taxa <- factor(taxa_flow_sig$taxa,
                           c('Birds','Mammals','Reptiles','Amphibians',
                             'Fish','Invertebrates','Plants/trees/shrubs',
                             'Multiple','Undefined'))

# effects level change
  taxa_flow_sig$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(taxa_flow_sig$sig_effect))
  taxa_flow_sig$sig_effect <- factor(taxa_flow_sig$sig_effect,
                             c('Positive','Neutral','Negative','Changed',
                               'Not Signif.',
                               'Unknown Signif.',
                               'Unclear'))

# telecoupling level change
  taxa_flow_sig$tele_cat <- factor(taxa_flow_sig$tele_cat,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Technology Transfer",
                                 "Tourism","Trade","Waste Transfer","Water Transfer",
                                 "Other","remove"))
```

Visualize as a matrix of pie charts

```{r}
# change colors
  #effect_cols <- c('#4EB265','#999999','#A50026','#FDB366','#9A709E')
  #effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  sig_effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141',
                       # include 'Not Signif.' and 'Unknown Signif.'
                       '#BBBBBB','#DDDDDD',
                       # 'unclear' keeps same color as before
                       '#882E72')
  
# Matrix of pie charts
  taxa_flow_fig <- ggplot(taxa_flow_sig) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(taxa ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ taxa, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('') 
                
# save image
  ggsave(taxa_flow_fig,
         filename=paste0(fig.dir,
                         # activate for vertical or horizontal version
                           #'synthesis_effects_taxa_and_flow_significant_Vert.png'),
                           'synthesis_effects_taxa_and_flow_significant_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  taxa_flow_fig
```

# 6. Second synthesis: Effects by coupling and metric categories

## 6.1 New dataset (long format)

Convert to long format, where metric is indicated.

```{r}
# subset
  metrics <- subset(s23,
                    select=c('paper_id','entry_id',
                            'taxa','tele_cat','effect',
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  metrics_long <- melt(metrics, id.vars=c('paper_id','entry_id',
                            'taxa','tele_cat','effect'))
  
# remove NA fields
  metrics_long <- metrics_long[!is.na(metrics_long$value),]
```

Rename last columns

```{r}
# change colnames
  colnames(metrics_long)[6] <- 'metric_type'
  colnames(metrics_long)[7] <- 'metric'
```

Rename metric types

```{r}
# check levels
  levels(metrics_long$metric_type)
```

```{r}
# change levels
  levels(metrics_long$metric_type) <- c('single species',
                                        'multiple species',
                                        'habitat')
```

Rename metrics

```{r}
# check levels
  levels(as.factor(metrics_long$metric))
```

```{r}
# remove parentheses
  metrics_long$metric <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metrics_long$metric))

# capitalize each word
  metrics_long$metric <- tools::toTitleCase(metrics_long$metric)
  
# adjust name
  metrics_long$metric <- gsub("With-in", 'Within',
                        as.character(metrics_long$metric))
  
# change levels, moving other to the end
  metrics_long$metric <- factor(metrics_long$metric,
                                c("Abundance/Density",
                                   "Amount",
                                   "Composition",
                                   "Detection",
                                   "Diversity Index",
                                   "Evenness",
                                   "Movement",
                                   "Occurrence",
                                   "Population Dynamics",
                                   "Quality",
                                   "Richness",
                                   "Within Species Diversity",
                                   "Other"))
  
# check levels
  levels(as.factor(metrics_long$metric))
```

## 6.2 Summary regardless of significance

### 6.2.1 Summary table

Make a new table summarizing dataset by metric, coupling category and effect

```{r}
# get summary
  metric_flow <- ddply(metrics_long,
                       .(metric_type, metric, tele_cat, effect),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
  write.csv(metric_flow, paste0(tab.dir,'synthesis_effects_metric_and_flow.csv'),
            row.names = TRUE)

# view
  metric_flow
```

Change levels

```{r}
# effects level change
  metric_flow$effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metric_flow$effect))
  metric_flow$effect <- factor(metric_flow$effect,
                             c('Positive','Neutral','Negative','Changed','Unclear'))

# telecoupling level change
  metric_flow$tele_cat <- factor(metric_flow$tele_cat,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Technology Transfer",
                                 "Tourism","Trade","Waste Transfer","Water Transfer",
                                 "Other","remove"))
```


### 6.2.2 Pie chart with all metrics combined

Visualize as a matrix of pie charts. First, **ALL** metrics together.

```{r}
# change colors
  effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  
# Matrix of pie charts
  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(metric_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_effects_metric_and_flow_Vert.png'),
                         'synthesis_effects_metric_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  metric_flow_fig
```

## 6.2.3 Pie chart separating metric categories

```{r}
# change colors
  effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  
# Matrix of pie charts
  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric_type ~ metric ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(metric_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_effects_metric_type_and_flow_Vert.png'),
                         'synthesis_effects_metric_type_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  metric_flow_fig
```

## 6.3 Summary emphasizing significance

### 6.3.1 New dataset (long format)

Convert to long format, where metric is indicated and the significant effect category is used instead.

```{r}
# subset
  sig_metrics <- subset(s23,
                    select=c('paper_id','entry_id',
                            'taxa','tele_cat',
                            'sig_effect', ##<--- THIS IS THE CHANGE HERE
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  sig_met_long <- melt(sig_metrics, id.vars=c('paper_id','entry_id',
                            'taxa','tele_cat','sig_effect'))
  
# remove NA fields
  sig_met_long <- sig_met_long[!is.na(sig_met_long$value),]
```

Rename last columns

```{r}
# change colnames
  colnames(sig_met_long)[6] <- 'metric_type'
  colnames(sig_met_long)[7] <- 'metric'
```

Rename metric types

```{r}
# check levels
  levels(sig_met_long$metric_type)
```

```{r}
# change levels
  levels(sig_met_long$metric_type) <- c('single species',
                                        'multiple species',
                                        'habitat')
```

Rename metrics

```{r}
# check levels
  levels(as.factor(sig_met_long$metric))
```

```{r}
# remove parentheses
  sig_met_long$metric <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(sig_met_long$metric))

# capitalize each word
  sig_met_long$metric <- tools::toTitleCase(sig_met_long$metric)
  
# adjust name
  sig_met_long$metric <- gsub("With-in", 'Within',
                        as.character(sig_met_long$metric))
  
# change levels, moving other to the end
  sig_met_long$metric <- factor(sig_met_long$metric,
                                c("Abundance/Density",
                                   "Amount",
                                   "Composition",
                                   "Detection",
                                   "Diversity Index",
                                   "Evenness",
                                   "Movement",
                                   "Occurrence",
                                   "Population Dynamics",
                                   "Quality",
                                   "Richness",
                                   "Within Species Diversity",
                                   "Other"))
  
# check levels
  levels(as.factor(sig_met_long$metric))
```

Make a new table summarizing dataset by metric, coupling category and significant effect

```{r}
# get summary
  met_flow_sig <- ddply(sig_met_long,
                       .(metric_type, metric, tele_cat, sig_effect),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
  write.csv(met_flow_sig,
            paste0(tab.dir,
                   'synthesis_effects_metric_and_flow_significant.csv'),
            row.names = FALSE)

# view
  met_flow_sig
```

Change levels

```{r}
# effects level change
  met_flow_sig$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(met_flow_sig$sig_effect))
  met_flow_sig$sig_effect <- factor(met_flow_sig$sig_effect,
                              c('Positive','Neutral','Negative','Changed',
                               'Not Signif.',
                               'Unknown Signif.',
                               'Unclear'))

# telecoupling level change
  met_flow_sig$tele_cat <- factor(met_flow_sig$tele_cat,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Technology Transfer",
                                 "Tourism","Trade","Waste Transfer","Water Transfer",
                                 "Other","remove"))
```

### 6.3.2 Pie chart with all metrics combined

Visualize as a matrix of pie charts. First, **ALL** metrics together.

```{r}
# Matrix of pie charts
  met_flow_sig_fig <- ggplot(met_flow_sig) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(met_flow_sig_fig,
         filename=paste0(fig.dir,
         # activate for vertical or horizontal version
           #'synthesis_effects_metric_and_flow_significant_Vert.png'),
           'synthesis_effects_metric_and_flow_significant_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  met_flow_sig_fig
```

## 6.3.3 Pie chart separating metric categories

```{r}
# Matrix of pie charts
  met_flow_sig_fig <- ggplot(met_flow_sig) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric_type ~ metric ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(met_flow_sig_fig,
         filename=paste0(fig.dir,
         # activate for vertical or horizontal version
           #'synthesis_effects_metric_type_and_flow_significant_Vert.png'),
           'synthesis_effects_metric_type_and_flow_significant_Horz.png'),
         height=6,width=14,units='in',
         dpi=600)


# display image
  met_flow_sig_fig
```





























```{r, eval=FALSE, echo=FALSE}

### JUNK BELOW #############

#library(gridExtra)
library(gtable)
gt = ggplot_gtable(ggplot_build(metric_flow_fig))
# gt$heights[10] = 4*gt$heights[10]
# grid.draw(gt)

gt <- ggplotGrob(metric_flow_fig)
gtable_show_layout(gt)
#grid::grid.show.layout(gt) 

pad <- gtable_add_padding(gt, unit(2, "cm"))
```
