---
title: 'MCBD: Synthesis of Metacoupled Effects on Biodiversity'
author: "Ciara Hovis, CSIS Lab, Michigan State University"
date: "September 16, 2020"
output: 
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Methods summary

Synthesis of survey 2 and 3 results for metacoupling/biodiversity systematic review. It consists of response summaries and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.2; R Core Team 2020) and its packages.

Load libraries, directories, and custom functions from source file.

```{r}
# Source file
  source('Reference.R')
```

Data is stored here:

```{r, echo=FALSE}
# Data directory
  dat.dir
```

Final tables are stored here:

```{r, echo=FALSE}
# Final tables
  tab.dir
```

Final figures are stored here:

```{r, echo=FALSE}
# Final figures
  fig.dir
```

For **this run** of the script, tables for manual checks will be stored in the following folder:

```{r, echo=FALSE}
tab.check.dir
```

# 3. Load data

```{r}
# surveys
  s1 <- read.csv(paste0(dat.dir,'survey1_cleaned.csv'))
  s2 <- read.csv(paste0(dat.dir,'survey2_cleaned_20200707.csv'))
  s3 <- read.csv(paste0(dat.dir,'survey3_cleaned.csv'))

  s23 <- read.csv(paste0(dat.dir,'s23.csv'))
  
```

Show column names

```{r}
# get col names
  colnames(s23)
```

# 4. Survey 1 Summary






# 5. Survey 2 & 3 Summary

## 5.1 Habitat Frequency 

By study

```{r}
# By study 

habitat.study <- count(s2, 'habitat')
print(habitat.study)
prop.table(table(s2$habitat))

# By entry (REPLICATED FLOW ID NOT RMVD YET)

habitat.entry <- count(s23, 'habitat')
print(habitat.entry)
prop.table(table(s23$habitat))


```



## 5.2 Taxa Frequency 


```{r}
# By study 
desired_length <- 8 
empty_list <- vector(mode = "list", length = desired_length)

taxa <- (s2$taxa)
taxa.list <- c('Mammals', 'Plants', 'Reptiles', 'Amphibians', 'Birds', 'Fish', 'Invertebrates', 'Other')
taxa.count <- empty_list

for (i in 1:length(taxa.list)) {
  
  taxa.count[i] <- sum(str_count(taxa, taxa.list[i]))
    }

taxa.count <- rbind(taxa.list,taxa.count)
taxa.count

multiple <- str_count(taxa, ';')
multiple <- multiple != 0
multiple <- table(multiple) ["TRUE"]


# By entry (REPLICATED FLOW ID NOT RMVD YET)

taxa.entry <- count(s23, 'taxa')
print(habitat.entry)
prop.table(table(s23$taxa))


```

## 5.3 Telecoupling Flow Category Frequency

```{r}
count(s2$tele_cat)

tc.list <- c("Energy Transfer", "Investment", "Knowledge Transfer", "Migration (human)", 
             "Migration (non-human)","Other", "remove", "Species Dispersal", "Technology Transfer",
             "Tourism", "Trade", "Water Transfer", "Waste Transfer")

desired_length <- length(tc.list)
empty_list <- vector(mode = "list", length = desired_length)


tc.cat <- (s2$tele_cat)
tc.count <- empty_list

for (i in 1:length(tc.list)) {
  
  tc.count[i] <- sum(str_count(tc.cat, tc.list[i]))
  
}

tc.count
tc.count <- as.data.frame(rbind(tc.list,tc.count))
tc.count

# Can't get loop to count the migration values for some reason, manual input code below

tc.table <- table(s2$tele_cat)

tc.count[2,4] <- tc.table[4] + tc.table[15]      # Migration (human) n=6
tc.count[2,5] <- tc.table[5]                     # Migration (non-human) n-7

tc.count

gather(tc.count)
```












Habitat vs sig_effect 


```{r}
# get summary
a <- ddply(s23, .(habitat, sig_effect), summarize,
           # total count of entries     
           count=length(habitat)) %>%
  # percents of effects within totals per hab
  group_by(habitat) %>%
  nest() %>% 
  mutate(perc_per_hab=map(data, function(x) x$count/sum(x$count))) %>% 
  unnest()


a

quick_plot <- ggplot(a, aes(fill=sig_effect, y=perc_per_hab, x=habitat)) + 
  geom_bar(position="stack", stat="identity") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  xlab("")

quick_plot

```


# 4. First synthesis: Effects of coupling categories across taxa 

## 4.1 Summary regardless of significance

Make a new table.

```{r}
# get summary
  taxa_flow <- ddply(s23, .(taxa, tele_cat, effect), summarize,
                # total count of entries     
                count=length(taxa)) %>%
                # percents of effects within totals per taxa
                group_by(taxa) %>%
                  nest() %>% 
                   mutate(perc_per_taxa=map(data, function(x) x$count/sum(x$count))) %>%
                    unnest()

# save as csv
  write.csv(taxa_flow, paste0(tab.dir,'synthesis_effects_taxa_and_flow.csv'),
            row.names = TRUE)

# view
  taxa_flow
```

Check levels

```{r}
levels(as.factor(taxa_flow$taxa))
```

Check levels

```{r}
levels(as.factor(taxa_flow$effect))
```
```{r}
levels(as.factor(taxa_flow$tele_cat))
```

Adjust levels

```{r}
# taxa level change
  taxa_flow$taxa <- factor(taxa_flow$taxa,
                           c('Birds','Mammals','Reptiles','Amphibians',
                             'Fish','Invertebrates','Plants/trees/shrubs',
                             'Multiple'))

# effects level change
  taxa_flow$effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(taxa_flow$effect))
  taxa_flow$effect <- factor(taxa_flow$effect,
                             c('Positive','Neutral','Negative','Changed','Unclear'))

# telecoupling level change
  taxa_flow$tele_cat <- factor(taxa_flow$tele_cat,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Technology Transfer",
                                 "Tourism","Trade","Waste Transfer","Water Transfer",
                                 "Other","remove"))
```
Energy Transfer            Investment    Knowledge Transfer 
                   63                    11                    73 
    Migration (human) Migration (non-human)                 Other 
                   16                    13                    10 
               remove     Species Dispersal   Technology Transfer 
                   15                    54                     1 
              Tourism                 Trade        Waste Transfer 
                  213                   286                     2 
       Water Transfer                  NA's 
                   12                    38 
Visualize as a matrix of pie charts

```{r}
# change colors
  #effect_cols <- c('#4EB265','#999999','#A50026','#FDB366','#9A709E')
  effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  
# Matrix of pie charts
  taxa_flow_fig <- ggplot(taxa_flow) + 
                    aes(x='', y = count, fill = effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(taxa ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ taxa, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y = element_text(size=10,
                                          angle=180, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('') 
                
# save image
  ggsave(taxa_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_effects_taxa_and_flow_Vert.png'),
                         'synthesis_effects_taxa_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  taxa_flow_fig
```

## 4.2 Summary emphasizing significance

Make a new column for significant effects; non-significant becomes a new level in this dataset.

```{r}
# new column of significant effects; non-significant effects renamed
  s23$sig_effect <- ''
  s23$sig_effect <- as.character(s23$significant)
  s23$effect <- as.character(s23$effect)
  s23$sig_effect[is.na(s23$sig_effect)] <- "Unknown Signif."
  s23$sig_effect[s23$sig_effect=='Not evaluated'] <- "Unknown Signif."
  s23$sig_effect[s23$sig_effect=='FALSE'] <- "Not Signif."
  s23$sig_effect[s23$sig_effect=='TRUE'] <- s23$effect[s23$sig_effect=='TRUE']
```

Summarize new column by taxa and telecoupling category.

```{r}
# get summary
  taxa_flow_sig <- ddply(s23, .(taxa, tele_cat, sig_effect), summarize,
                        # total count of entries     
                        count=length(taxa))
# save as csv
  write.csv(taxa_flow_sig,
            paste0(tab.dir,'synthesis_effects_taxa_and_flow_significant.csv'),
            row.names = TRUE)

# view
  taxa_flow_sig
```

Change levels

```{r}
# taxa level change
  taxa_flow_sig$taxa <- factor(taxa_flow_sig$taxa,
                           c('Birds','Mammals','Reptiles','Amphibians',
                             'Fish','Invertebrates','Plants/trees/shrubs',
                             'Multiple','Undefined'))

# effects level change
  taxa_flow_sig$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(taxa_flow_sig$sig_effect))
  taxa_flow_sig$sig_effect <- factor(taxa_flow_sig$sig_effect,
                             c('Positive','Neutral','Negative','Changed',
                               'Not Signif.',
                               'Unknown Signif.',
                               'Unclear'))

# telecoupling level change
  taxa_flow_sig$tele_cat <- factor(taxa_flow_sig$tele_cat,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Technology Transfer",
                                 "Tourism","Trade","Waste Transfer","Water Transfer",
                                 "Other","remove"))
```

Visualize as a matrix of pie charts

```{r}
# change colors
  #effect_cols <- c('#4EB265','#999999','#A50026','#FDB366','#9A709E')
  #effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  sig_effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141',
                       # include 'Not Signif.' and 'Unknown Signif.'
                       '#BBBBBB','#DDDDDD',
                       # 'unclear' keeps same color as before
                       '#882E72')
  
# Matrix of pie charts
  taxa_flow_fig <- ggplot(taxa_flow_sig) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(taxa ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ taxa, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('') 
                
# save image
  ggsave(taxa_flow_fig,
         filename=paste0(fig.dir,
                         # activate for vertical or horizontal version
                           #'synthesis_effects_taxa_and_flow_significant_Vert.png'),
                           'synthesis_effects_taxa_and_flow_significant_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  taxa_flow_fig
```

# 5. Second synthesis: Effects by coupling and metric categories

## 5.1 New dataset (long format)

Convert to long format, where metric is indicated.

```{r}
# subset
  metrics <- subset(s23,
                    select=c('paper_id','entry_id',
                            'taxa','tele_cat','effect',
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  metrics_long <- melt(metrics, id.vars=c('paper_id','entry_id',
                            'taxa','tele_cat','effect'))
  
# remove NA fields
  metrics_long <- metrics_long[!is.na(metrics_long$value),]
```

Rename last columns

```{r}
# change colnames
  colnames(metrics_long)[6] <- 'metric_type'
  colnames(metrics_long)[7] <- 'metric'
```

Rename metric types

```{r}
# check levels
  levels(metrics_long$metric_type)
```

```{r}
# change levels
  levels(metrics_long$metric_type) <- c('single species',
                                        'multiple species',
                                        'habitat')
```

Rename metrics

```{r}
# check levels
  levels(as.factor(metrics_long$metric))
```

```{r}
# remove parentheses
  metrics_long$metric <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metrics_long$metric))

# capitalize each word
  metrics_long$metric <- tools::toTitleCase(metrics_long$metric)
  
# adjust name
  metrics_long$metric <- gsub("With-in", 'Within',
                        as.character(metrics_long$metric))
  
# change levels, moving other to the end
  metrics_long$metric <- factor(metrics_long$metric,
                                c("Abundance/Density",
                                   "Amount",
                                   "Composition",
                                   "Detection",
                                   "Diversity Index",
                                   "Evenness",
                                   "Movement",
                                   "Occurrence",
                                   "Population Dynamics",
                                   "Quality",
                                   "Richness",
                                   "Within Species Diversity",
                                   "Other"))
  
# check levels
  levels(as.factor(metrics_long$metric))
```

## 5.2 Summary regardless of significance

### 5.2.1 Summary table

Make a new table summarizing dataset by metric, coupling category and effect

```{r}
# get summary
  metric_flow <- ddply(metrics_long,
                       .(metric_type, metric, tele_cat, effect),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
  write.csv(metric_flow, paste0(tab.dir,'synthesis_effects_metric_and_flow.csv'),
            row.names = TRUE)

# view
  metric_flow
```

Change levels

```{r}
# effects level change
  metric_flow$effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metric_flow$effect))
  metric_flow$effect <- factor(metric_flow$effect,
                             c('Positive','Neutral','Negative','Changed','Unclear'))

# telecoupling level change
  metric_flow$tele_cat <- factor(metric_flow$tele_cat,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Technology Transfer",
                                 "Tourism","Trade","Waste Transfer","Water Transfer",
                                 "Other","remove"))
```


### 5.2.2 Pie chart with all metrics combined

Visualize as a matrix of pie charts. First, **ALL** metrics together.

```{r}
# change colors
  effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  
# Matrix of pie charts
  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(metric_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_effects_metric_and_flow_Vert.png'),
                         'synthesis_effects_metric_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  metric_flow_fig
```

## 5.2.3 Pie chart separating metric categories

```{r}
# change colors
  effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  
# Matrix of pie charts
  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric_type ~ metric ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(metric_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_effects_metric_type_and_flow_Vert.png'),
                         'synthesis_effects_metric_type_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  metric_flow_fig
```

## 5.3 Summary emphasizing significance

### 5.3.1 New dataset (long format)

Convert to long format, where metric is indicated and the significant effect category is used instead.

```{r}
# subset
  sig_metrics <- subset(s23,
                    select=c('paper_id','entry_id',
                            'taxa','tele_cat',
                            'sig_effect', ##<--- THIS IS THE CHANGE HERE
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  sig_met_long <- melt(sig_metrics, id.vars=c('paper_id','entry_id',
                            'taxa','tele_cat','sig_effect'))
  
# remove NA fields
  sig_met_long <- sig_met_long[!is.na(sig_met_long$value),]
```

Rename last columns

```{r}
# change colnames
  colnames(sig_met_long)[6] <- 'metric_type'
  colnames(sig_met_long)[7] <- 'metric'
```

Rename metric types

```{r}
# check levels
  levels(sig_met_long$metric_type)
```

```{r}
# change levels
  levels(sig_met_long$metric_type) <- c('single species',
                                        'multiple species',
                                        'habitat')
```

Rename metrics

```{r}
# check levels
  levels(as.factor(sig_met_long$metric))
```

```{r}
# remove parentheses
  sig_met_long$metric <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(sig_met_long$metric))

# capitalize each word
  sig_met_long$metric <- tools::toTitleCase(sig_met_long$metric)
  
# adjust name
  sig_met_long$metric <- gsub("With-in", 'Within',
                        as.character(sig_met_long$metric))
  
# change levels, moving other to the end
  sig_met_long$metric <- factor(sig_met_long$metric,
                                c("Abundance/Density",
                                   "Amount",
                                   "Composition",
                                   "Detection",
                                   "Diversity Index",
                                   "Evenness",
                                   "Movement",
                                   "Occurrence",
                                   "Population Dynamics",
                                   "Quality",
                                   "Richness",
                                   "Within Species Diversity",
                                   "Other"))
  
# check levels
  levels(as.factor(sig_met_long$metric))
```

Make a new table summarizing dataset by metric, coupling category and significant effect

```{r}
# get summary
  met_flow_sig <- ddply(sig_met_long,
                       .(metric_type, metric, tele_cat, sig_effect),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
  write.csv(met_flow_sig,
            paste0(tab.dir,
                   'synthesis_effects_metric_and_flow_significant.csv'),
            row.names = FALSE)

# view
  met_flow_sig
```

Change levels

```{r}
# effects level change
  met_flow_sig$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(met_flow_sig$sig_effect))
  met_flow_sig$sig_effect <- factor(met_flow_sig$sig_effect,
                              c('Positive','Neutral','Negative','Changed',
                               'Not Signif.',
                               'Unknown Signif.',
                               'Unclear'))

# telecoupling level change
  met_flow_sig$tele_cat <- factor(met_flow_sig$tele_cat,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Technology Transfer",
                                 "Tourism","Trade","Waste Transfer","Water Transfer",
                                 "Other","remove"))
```

### 5.3.2 Pie chart with all metrics combined

Visualize as a matrix of pie charts. First, **ALL** metrics together.

```{r}
# Matrix of pie charts
  met_flow_sig_fig <- ggplot(met_flow_sig) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(met_flow_sig_fig,
         filename=paste0(fig.dir,
         # activate for vertical or horizontal version
           #'synthesis_effects_metric_and_flow_significant_Vert.png'),
           'synthesis_effects_metric_and_flow_significant_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  met_flow_sig_fig
```

## 5.3.3 Pie chart separating metric categories

```{r}
# Matrix of pie charts
  met_flow_sig_fig <- ggplot(met_flow_sig) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric_type ~ metric ~ tele_cat, switch='y') + #horizontal
                      #facet_grid(tele_cat ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(met_flow_sig_fig,
         filename=paste0(fig.dir,
         # activate for vertical or horizontal version
           #'synthesis_effects_metric_type_and_flow_significant_Vert.png'),
           'synthesis_effects_metric_type_and_flow_significant_Horz.png'),
         height=6,width=14,units='in',
         dpi=600)


# display image
  met_flow_sig_fig
```
# 7. Standardization

Some papers/studies reported multiple metrics. If left as is, our results may be misleading as some studies only reported 1 or 2 biodiversity metric impacts, while others reported many (>100). To address this, we will create a "majority" effect value for each unique study ID.

```{r}

# what is the range of number of metric/entries?
num.entry <- as.data.frame(x= table(s23$paper_id) )
mean(num.entry$Freq)
median(num.entry$Freq)
max(num.entry$Freq)

# how many instances are paper_id & entry_id repeated due to separating the TC.Flow

flow.rep <- paste(s23$paper_id, s23$entry_id, sep="_")
flow.rep <- as.data.frame(table(flow.rep))
flow.rep[flow.rep$freq > 1,]

```
