---
title: 'MCBD: Synthesis of Metacoupled sig_effects on Biodiversity'
author: "Veronica F. Frans, CSIS Lab, Michigan State University"
date: "May 30, 2020 (Updated: September 4, 2020)"
output: 
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: true
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Methods summary

Synthesis of survey 2 and 3 results for metacoupling/biodiversity systematic review. It consists of error checks, response summaries, and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.2; R Core Team 2020) and its packages.

Load libraries, directories, and custom functions from source file.

```{r}
# Source file
  source('./scripts/Reference.R')
```

Data is stored here:

```{r, echo=FALSE}
# Data directory
  dat.dir
```

Final tables are stored here:

```{r, echo=FALSE}
# Final tables
  tab.dir
```

Final figures are stored here:

```{r, echo=FALSE}
# Final figures
  fig.dir
```



# 3. Load data

```{r}
# surveys
  s23 <- read.csv(paste0(dat.dir,'s23.csv'))
```

Show column names

```{r}
# get col names
  colnames(s23)
```

Replicate TC flows

```{r}
# set as character
  s23$tc <- as.character(s23$tc)
  table(s23$tc)   # no NAs until rows get separated
  poo<-s23[is.na(s23$tc),]
  
  
# show original length of rows
  print(paste('Original number of rows:',nrow(s23)))

# split multiple flows listed in a row into other new rows
  tcRep <- separate_rows(s23, tc, sep=";", convert = TRUE)
  tcRep$tc <- as.factor(tcRep$tc)

# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(tcRep)))
  
  tcRep_maj <- tcRep[!duplicated(tcRep$paper_id),]


```


# 4. First synthesis: sig_effects of coupling categories across taxa 

## 4.1 Summary regardless of significance

Make a new table.

```{r}
# get summary
  taxa_flow <- ddply(tcRep, .(taxa, tc, sig_effect), summarize,
                # total count of entries     
                count=length(taxa)) %>%
                # percents of sig_effects within totals per taxa
                group_by(taxa) %>%
                  nest() %>% 
                   mutate(perc_per_taxa=map(data, function(x) x$count/sum(x$count))) %>%
                    unnest()

# save as csv
  write.csv(taxa_flow, paste0(tab.dir,'synthesis_sig_effects_taxa_and_flow.csv'),
            row.names = TRUE)

# view
  taxa_flow
```

Check levels

```{r}
levels(as.factor(taxa_flow$taxa))
```

Check levels

```{r}
levels(as.factor(taxa_flow$sig_effect))
```
```{r}
levels(as.factor(taxa_flow$tc))
```

Adjust levels

```{r}
# taxa level change
  taxa_flow$taxa <- factor(taxa_flow$taxa,
                           c('Birds','Mammals','Reptiles','Amphibians',
                             'Fish','Invertebrates','Plants/Trees/Shrubs',
                             'Multiple'))

# sig_effects level change
  taxa_flow$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(taxa_flow$sig_effect))
  taxa_flow$sig_effect <- factor(taxa_flow$sig_effect,
                             c( "Beneficial","Changed","Detrimental","No relation or unclear"))

# telecoupling level change
  taxa_flow$tc <- factor(taxa_flow$tc,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
```

Visualize as a matrix of pie charts

```{r}
# change colors
  #sig_effect_cols <- c('#4EB265','#999999','#A50026','#FDB366','#9A709E')
  #sig_effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  sig_effect_cols <- sigeff_col

# Matrix of pie charts
  taxa_flow_fig <- ggplot(taxa_flow) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(taxa ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ taxa, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y = element_text(size=10,
                                          angle=180, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('') 
                
# save image
  ggsave(taxa_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_sig_effects_taxa_and_flow_Vert.png'),
                         'synthesis_sig_effects_taxa_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  taxa_flow_fig
```

Study level

Make a new table.

```{r}
# get summary
  taxa_flow <- ddply(tcRep_maj, .(taxa, tc, maj_eff), summarize,
                # total count of entries     
                count=length(taxa)) %>%
                # percents of sig_effects within totals per taxa
                group_by(taxa) %>%
                  nest() %>% 
                   mutate(perc_per_taxa=map(data, function(x) x$count/sum(x$count))) %>%
                    unnest()

# save as csv
  write.csv(taxa_flow, paste0(tab.dir,'synthesis_maj_eff_taxa_and_flow.csv'),
            row.names = TRUE)

# view
  taxa_flow
```

Check levels

```{r}
levels(as.factor(taxa_flow$taxa))
```

Check levels

```{r}
levels(as.factor(taxa_flow$maj_eff))
```
```{r}
levels(as.factor(taxa_flow$tc))
```

Adjust levels

```{r}
# taxa level change
  taxa_flow$taxa <- factor(taxa_flow$taxa,
                           c('Birds','Mammals','Reptiles','Amphibians',
                             'Fish','Invertebrates','Plants/Trees/Shrubs',
                             'Multiple'))

# sig_effects level change
  taxa_flow$maj_eff <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(taxa_flow$maj_eff))
  taxa_flow$maj_eff <- factor(taxa_flow$maj_eff,
                             c( "Beneficial","Changed","Detrimental","No relation or unclear"))

# telecoupling level change
  taxa_flow$tc <- factor(taxa_flow$tc,
                               c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
```

Visualize as a matrix of pie charts

```{r}
# change colors
  #sig_effect_cols <- c('#4EB265','#999999','#A50026','#FDB366','#9A709E')
  #sig_effect_cols <- c('#4EB265','#777777','#DC050C','#F6C141','#882E72')
  sig_effect_cols <- sigeff_col

# Matrix of pie charts
  taxa_flow_fig <- ggplot(taxa_flow) + 
                    aes(x='', y = count, fill = maj_eff) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(taxa ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ taxa, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y = element_text(size=10,
                                          angle=180, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('') 
                
# save image
  ggsave(taxa_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_sig_effects_taxa_and_flow_Vert.png'),
                         'synthesis_maj_eff_taxa_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  taxa_flow_fig
```




# 5. Second synthesis: sig_effects by coupling and metric categories

## 5.1 New dataset (long format)

Convert to long format, where metric is indicated.

```{r}
# subset
  metrics <- subset(tcRep,
                    select=c('paper_id','entry_id',
                            'taxa','tc','sig_effect',
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  metrics_long <- melt(metrics, id.vars=c('paper_id','entry_id',
                            'taxa','tc','sig_effect'))
  
# remove NA fields
  metrics_long <- metrics_long[!is.na(metrics_long$value),]
```

Rename last columns

```{r}
# change colnames
  colnames(metrics_long)[6] <- 'metric_type'
  colnames(metrics_long)[7] <- 'metric'
```

Rename metric types

```{r}
# check levels
  levels(metrics_long$metric_type)
```

```{r}
# change levels
  levels(metrics_long$metric_type) <- c('single species',
                                        'multiple species',
                                        'habitat')
```

Rename metrics

```{r}
# check levels
  levels(as.factor(metrics_long$metric))
```

```{r}
# remove parentheses
  metrics_long$metric <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metrics_long$metric))

# capitalize each word
  metrics_long$metric <- tools::toTitleCase(metrics_long$metric)
  
# adjust name
  metrics_long$metric <- gsub("With-in", 'Within',
                        as.character(metrics_long$metric))
  
# change levels, moving other to the end
  metrics_long$metric <- factor(metrics_long$metric,
                                c("Abundance/Density",
                                   "Amount",
                                   "Composition",
                                   "Detection",
                                   "Diversity Index",
                                   "Evenness",
                                   "Movement",
                                   "Occurrence",
                                   "Population Dynamics",
                                   "Quality",
                                   "Richness",
                                   "Within Species Diversity"
                                  ))
  
# check levels
  levels(as.factor(metrics_long$metric))
```

## 5.2 Summary regardless of significance

### 5.2.1 Summary table

Make a new table summarizing dataset by metric, coupling category and sig_effect

```{r}
# get summary
  metric_flow <- ddply(metrics_long,
                       .(metric_type, metric, tc, sig_effect),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
  write.csv(metric_flow, paste0(tab.dir,'synthesis_sig_effects_metric_and_flow.csv'),
            row.names = TRUE)

# view
  metric_flow
```

Change levels

```{r}
# sig_effects level change
  metric_flow$sig_effect <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metric_flow$sig_effect))
  metric_flow$sig_effect <- factor(metric_flow$sig_effect,
                             c( "Beneficial","Changed","Detrimental","Not significant or unclear"))
# telecoupling level change
  metric_flow$tc <- factor(metric_flow$tc,
                                c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
  
```


### 5.2.2 Pie chart with all metrics combined

Visualize as a matrix of pie charts. First, **ALL** metrics together.

```{r}

# Matrix of pie charts
  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(metric_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_sig_effects_metric_and_flow_Vert.png'),
                         'synthesis_sig_effects_metric_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  metric_flow_fig
```

## 5.2.3 Pie chart separating metric categories

```{r}
# Matrix of pie charts
  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = sig_effect) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric_type ~ metric ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(metric_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_sig_effects_metric_type_and_flow_Vert.png'),
                         'synthesis_sig_effects_metric_type_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  metric_flow_fig
```








Study level


Convert to long format, where metric is indicated.

```{r}
# subset
  metrics <- subset(tcRep_maj,
                    select=c('paper_id','entry_id',
                            'taxa','tc','maj_eff',
                            'biodiv_cat_1sp',
                            'biodiv_cat_multsp',
                            'biodiv_cat_habitat'))
# melt
  metrics_long <- melt(metrics, id.vars=c('paper_id','entry_id',
                            'taxa','tc','maj_eff'))
  
# remove NA fields
  metrics_long <- metrics_long[!is.na(metrics_long$value),]
```

Rename last columns

```{r}
# change colnames
  colnames(metrics_long)[6] <- 'metric_type'
  colnames(metrics_long)[7] <- 'metric'
```

Rename metric types

```{r}
# check levels
  levels(metrics_long$metric_type)
```

```{r}
# change levels
  levels(metrics_long$metric_type) <- c('single species',
                                        'multiple species',
                                        'habitat')
```

Rename metrics

```{r}
# check levels
  levels(as.factor(metrics_long$metric))
```

```{r}
# remove parentheses
  metrics_long$metric <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metrics_long$metric))

# capitalize each word
  metrics_long$metric <- tools::toTitleCase(metrics_long$metric)
  
# adjust name
  metrics_long$metric <- gsub("With-in", 'Within',
                        as.character(metrics_long$metric))
  
# change levels, moving other to the end
  metrics_long$metric <- factor(metrics_long$metric,
                                c("Abundance/Density",
                                   "Amount",
                                   "Composition",
                                   "Detection",
                                   "Diversity Index",
                                   "Evenness",
                                   "Movement",
                                   "Occurrence",
                                   "Population Dynamics",
                                   "Quality",
                                   "Richness",
                                   "Within Species Diversity"
                                  ))
  
# check levels
  levels(as.factor(metrics_long$metric))
```



```{r}
# get summary
  metric_flow <- ddply(metrics_long,
                       .(metric_type, metric, tc, maj_eff),
                       summarize,
                      # total count of entries     
                        count=length(metric))

# save as csv
  write.csv(metric_flow, paste0(tab.dir,'synthesis_maj_eff_metric_and_flow.csv'),
            row.names = TRUE)

# view
  metric_flow
```

Change levels

```{r}
# sig_effects level change
  metric_flow$maj_eff <- gsub("\\s*\\([^\\)]+\\)", '',
                          as.character(metric_flow$maj_eff))
  metric_flow$maj_eff <- factor(metric_flow$maj_eff,
                             c( "Beneficial","Changed","Detrimental","No relation or unclear"))
# telecoupling level change
  metric_flow$tc <- factor(metric_flow$tc,
                                c("Energy Transfer","Investment","Knowledge Transfer",
                                 "Migration (human)","Migration (non-human)",
                                 "Species Dispersal","Tourism","Trade","Waste Transfer","Water Transfer"
                                ))
  
```


### 5.2.2 Pie chart with all metrics combined

Visualize as a matrix of pie charts. First, **ALL** metrics together.

```{r}

# Matrix of pie charts
  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = maj_eff) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(metric_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_sig_effects_metric_and_flow_Vert.png'),
                         'synthesis_sig_effects_metric_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  metric_flow_fig
```

## 5.2.3 Pie chart separating metric categories

```{r}
# Matrix of pie charts
  metric_flow_fig <- ggplot(metric_flow) + 
                    aes(x='', y = count, fill = maj_eff) +
                    geom_bar(position='fill',
                             stat='identity', width = 1, size = 0.01) +
                    # activate for vertical or horizontal version
                      facet_grid(metric_type ~ metric ~ tc, switch='y') + #horizontal
                      #facet_grid(tc ~ metric, switch='y') +  #vertical
                    # convert to pie chart
                      coord_polar(theta = 'y') +
                    # colors
                      scale_fill_manual(
                        values=sig_effect_cols,
                        guide = guide_legend(reverse = FALSE))  + 
                        scale_y_discrete(position='right',expand=c(0,0))+
                    # style
                      theme_gray(base_size=10)+
                      theme(
                        axis.title=element_blank(),
                        axis.line=element_blank(),
                        axis.ticks=element_blank(),
                        axis.text=element_blank(),
                        panel.border = element_blank(),
                        panel.grid=element_blank(),
                        panel.grid.major = element_blank(),
                        panel.grid.minor = element_blank(),
                        plot.background = element_rect(),
                        plot.title=element_blank(),
                        strip.text.x = element_text(size=10,
                                          angle=90, vjust=0, hjust = 0),
                        strip.text.y.left = element_text(size=10,
                                          angle=0, vjust=0, hjust = 0),
                        strip.background = element_rect(fill='white'),
                        panel.spacing = unit(0.1, 'lines')
                        ) +
                    # labels
                      ylab('') + xlab('')
                
# save image
  ggsave(metric_flow_fig,
         filename=paste0(fig.dir,
                         #'synthesis_sig_effects_metric_type_and_flow_Vert.png'),
                         'synthesis_maj_eff_metric_type_and_flow_Horz.png'),
         #height=6.5,width=7,units='in',
         dpi=600)


# display image
  metric_flow_fig
```

Heatmap

```{r}

# Load data of number of studies by taxa and flow
nr_taxa_tele <- aggregate(x = taxa_flow$count,
                               by = list(taxa_flow$taxa, taxa_flow$tc),
                               FUN = sum)

 

# Rename columns

names(nr_taxa_tele)[1:3] <- c("taxa", "telecoupling", "count")

   

# Fill the gaps

mat_nr_taxa_tele <-dcast(nr_taxa_tele, taxa ~ telecoupling, value.var = 'count')
filled_nr_taxa_tele <- melt(mat_nr_taxa_tele, id=c("taxa"))
filled_nr_taxa_tele[is.na(filled_nr_taxa_tele)] <- 0
names(filled_nr_taxa_tele)[2:3] <- c("telecoupling", "count")

# Create 'count' categories for representation

filled_nr_taxa_tele$count_factor <- cut(filled_nr_taxa_tele$count,

          breaks = c(-1,0,5,10,20,50,100,max(filled_nr_taxa_tele$count,na.rm=T)),              labels=c("0","1-5","5-10","10-20","20-50","50-100",">100"))


# Change order of factor levels for consistency with other figures

filled_nr_taxa_tele$taxa <- factor(filled_nr_taxa_tele$taxa,
          levels=c("Multiple","Invertebrates","Fish","Amphibians","Reptiles","Mammals",
                  "Birds"))

   

# Heatmap plot

heatmap_teletaxa <- ggplot(filled_nr_taxa_tele,
                      aes(x=telecoupling, y=taxa, fill=count_factor)) +
                      geom_tile(color = "white", size=0.25) +
                    scale_fill_manual(values=c("grey90","#BCDDF5","#8FCBF5","#4EA6E6",
                                               "#4E91CC","#3F76A6","#274866"))+
                    labs(x="",y="")+
                    scale_y_discrete(expand=c(0,0))+
                    theme_grey(base_size=8)+                

                    theme(legend.title = element_text(size = 10),
                      legend.text = element_text(size = 10, face="bold"),
                      plot.background=element_blank(),
                      plot.title = element_blank(),
                      axis.title= element_blank(),
                      axis.ticks = element_blank(),
                      axis.text.x.top = element_text(size=10, angle = 90, vjust=0,
                                                     hjust = 0),
                      axis.text.y.left = element_text(size=10, angle = 360, vjust=0.5,
                                                      hjust = 0),
                      strip.background = element_rect(fill="white"),
                      panel.spacing = unit(0.1, "lines")) +
                    scale_x_discrete(position = "top") +
                    labs(fill = "number of entries")

                    heatmap_teletaxa

                   

# Display image

heatmap_teletaxa

 

      

```


