---
author: "Ciara Hovis & Veronica F. Frans, CSIS Lab, Michigan State University"
date: "May 30, 2020 (Updated: October 19, 2020)"
output: 
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: true
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Methods summary

Synthesis of survey 2 and 3 results for metacoupling/biodiversity systematic review. It consists of error checks, response summaries, and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.2; R Core Team 2020) and its packages.

Load libraries, directories, and custom functions from source file.

```{r}
# Source file
  source('./scripts/Reference.R')
```

Data is stored here:

```{r, echo=FALSE}
# Data directory
  dat.dir
```

Final tables are stored here:

```{r, echo=FALSE}
# Final tables
  tab.dir
```

Final figures are stored here:

```{r, echo=FALSE}
# Final figures
  fig.dir
```


# 3. Load data


```{r}
# load previous workspace (if needed)
  #load("synthesisResults.RData")

# surveys
  survey2 <- read.csv(paste0(dat.dir,'survey2_cleaned.csv'))
  survey3 <- read.csv(paste0(dat.dir,'survey3_cleaned.csv'))
```

# 4. Data formatting

## 4.1 Merge tables

Merge tables. The expected length of this merge should be the same as survey 3, with fields from survey 2 repeated across entries for each paper id. 

```{r}
# left join survey 2 to survey 3
survey3$hab <- NA
hab.table <- as.data.frame(cbind(survey2$paper_id, survey2$habitat))
survey3$hab <- hab.table$V2[match(survey3$paper_id,hab.table$V1)]
survey3$tc <-NA
tc.table <- as.data.frame(cbind(survey2$paper_id, survey2$tele_cat))
survey3$tc <- tc.table$V2[match(survey3$paper_id,tc.table$V1)]

s23 <- left_join(survey3,survey2,by=c("paper_id","coder_id"))
```

Show column names

```{r}
# get col names
  colnames(s23)
```

Drop columns. Includes s3 notes now.

```{r}
unwanted <- c(# survey 3 fields
              'timestamp.x','taxa.x',
              # survey 2 fields
              'coder_id','entry','final_decision','X',
              'taxa.y', 'timestamp.y', 'year_pub', 'author',
              'taxa_list', 'num_time_pd', 'year_start',
              'year_end','temp_res','temp_res_unk',
              'b4_dur_after','comments','further_discuss'
              )

s23$taxa <- s23$taxa.x
s23$sig_effect <- '' #adding column now because there are errors below

s23 <- s23 %>%
        select(-one_of(unwanted))
```

## 4.2 Quick cleanup of levels

Next, show levels of couplings

```{r}
levels(as.factor(s23$tele_cat))
```

Fix paper 3081 based on CLH notes (10/7/2020)

```{r}
#need to change tele cat and effect for both entries
s23[which(s23$paper_id == 3081 & s23$entry_id == 1),]

s23$tc[which(s23$paper_id == 3081 & s23$entry_id == 1)] <- 'Trade;Knowledge Transfer'   # change tc to just trade and knowledge 
s23$tc[which(s23$paper_id == 3081 & s23$entry_id == 2)] <- 'Tourism'                    # change tc to just tourism
  
```

# 6. Classify Impact and Significance Category

To simplify our results, we opted classify impacts into 4 categories:  Positive, Negative, Comp. Change, No relation or unclear.

## 6.1 Investigate Significance Not Evaluated

No action taken yet, need to discuss with group

```{r}
# Check how many entries were "not evaluated" n=259
table(s23$significant)

# subset and drop last row (all NAs)
not.eval <- s23[s23$significant == "Not evaluated",]
not.eval <- not.eval[-nrow(not.eval),]
  
# How many paper IDs? n=57
length(unique(not.eval$paper_id))
unique(not.eval$paper_id)

# Look at impacts and metric type
table(not.eval$biodiv_cat_1sp)
table(not.eval$biodiv_cat_multsp)
table(not.eval$biodiv_cat_habitat)
table(not.eval$effect)

```


## 6.2  Classification Code

```{r}



  for(i in 1:nrow(s23)) {
  
    # positive impact AND True/NotEval Sig == POSITIVE
    if(s23$effect[i] == 'Positive (beneficial)' &&
       (s23$significant[i] == 'TRUE' || s23$significant[i] == 'Not evaluated') )
    {
    s23$sig_effect[i] = 'Beneficial';
    }

    # negative impact AND True/NotEval Sig == NEGATIVE
    else if(s23$effect[i] == 'Negative (detrimental)' &&
       (s23$significant[i] == 'TRUE' || s23$significant[i] == 'Not evaluated') )
    {
    s23$sig_effect[i] = 'Harmful';
    }

    # changed impact AND True/NotEval Sig == CHANGED
    else if(s23$effect[i] == 'Changed (e.g. species composition)' &&
    (s23$significant[i] == 'TRUE' || s23$significant[i] == 'Not evaluated') )
    {
    s23$sig_effect[i] = 'Changed';
    }

    else
    {
    s23$sig_effect[i] = 'Not significant or unclear';
    }

  }

# Check if loop worked

check_sig_effect <- as.data.frame(cbind(s23$effect, s23$significant, s23$sig_effect))

# Look at distribution

table(s23$sig_effect)

```

Create Majority Effect Column

Some papers/studies reported multiple metrics. If left as is, our results may be misleading as some studies only reported 1 or 2 biodiversity metric impacts, while others reported many (>100). To address this, we will create a "majority" effect value for each unique study ID.


```{r}

Mode <- function(x) {
    tabulatedOutcomes <- table(x)
    sortedOutcomes <- sort(tabulatedOutcomes, decreasing=TRUE)
    mostCommonLabel <- names(sortedOutcomes)[1]
    mostCommonLabel
}

table(s23$paper_id,s23$sig_effect)

maj_effect <- s23 %>%
    dplyr::select(paper_id, sig_effect) %>%
    ungroup() %>%
    group_by(paper_id) %>%
    add_tally(name = 'total_sigeff') %>%
    dplyr::ungroup() %>%
    dplyr::group_by(paper_id, total_sigeff) %>%
    dplyr::mutate(maj_effect = Mode(sig_effect)) %>%
    arrange(paper_id) 

maj_effect2 <- s23 %>%
    dplyr::select(paper_id, sig_effect) %>%
    ungroup() %>%
    group_by(paper_id) %>%
    add_tally(name = 'total_sigeff') %>%
    dplyr::ungroup() %>%
    dplyr::group_by(paper_id, total_sigeff) %>%
    dplyr::count(sig_effect, name = 'n_sigeff') %>%
    arrange(paper_id) %>%
    dplyr::mutate(pct_sigeff = n_sigeff/total_sigeff*100) %>% 
    ungroup()

s23$maj_eff <- maj_effect$maj_effect

maj_effect2$maj_eff <- NA
maj.table <- as.data.frame(cbind(maj_effect$paper_id, maj_effect$maj_effect))
maj.table<-maj.table[!duplicated(maj.table),]


maj_effect2$maj_eff <- maj.table$V2[match(maj_effect2$paper_id,maj.table$V1)]

# Deal with ties

for (i in 1:nrow(maj_effect2)){
  
    x <- maj_effect2[which(maj_effect2$paper_id == maj_effect2$paper_id[i]), 5]
    ifelse(var(x) == 0, maj_effect2$maj_eff[i] <- 'Mixed', maj_effect2$maj_eff[i] <- maj_effect2$maj_eff[i])
  }

write.csv(maj_effect2, paste0(tab.dir, 'maj_effect.csv'))

maj_effect3 <- cbind(maj_effect2$paper_id,maj_effect2$maj_eff)
maj_effect3 <- as.data.frame(maj_effect3)
maj_effect3 <- maj_effect3[!duplicated(maj_effect3),]

s23$maj_eff <- maj_effect3$V2[match(s23$paper_id, maj_effect3$V1)]


```

Determine Majority effect by paper and taxa  

```{r}
# repeat taxa rows

taxID <- s23
taxID$tax_ID <- paste0(taxID$paper_id,'_',taxID$taxa)
nrow(taxID)
length(unique(taxID$paper_id))    # number of papers n=127
length(unique(taxID$tax_ID))       # number of paper:taxa n=132
length(unique(taxID$tax_ID)) - length(unique(taxID$paper_id))  # number of papers with multiple taxa (n=5)       

q <- as.data.frame(table(unique(taxID$tax_ID))) 

p <- q %>% tidyr::separate(Var1, c("ID"), extra='drop')

q <-cbind(p,q)
m <- as.data.frame(table(q$ID))
n <- m[which(m$Freq >1),] # paper_ids reporting >1 taxa metric


# Determine sig_effect based on tax_ID, rather than paper_ID

maj_effect_taxa <- taxID %>%
    dplyr::select(tax_ID, sig_effect) %>%
    ungroup() %>%
    group_by(tax_ID) %>%
    add_tally(name = 'total_sigeff') %>%
    dplyr::ungroup() %>%
    dplyr::group_by(tax_ID, total_sigeff) %>%
    dplyr::mutate(maj_eff_taxa = Mode(sig_effect)) %>%
    arrange(tax_ID) 

maj_effect2_taxa <- taxID %>%
    dplyr::select(tax_ID, sig_effect) %>%
    ungroup() %>%
    group_by(tax_ID) %>%
    add_tally(name = 'total_sigeff') %>%
    dplyr::ungroup() %>%
    dplyr::group_by(tax_ID, total_sigeff) %>%
    dplyr::count(sig_effect, name = 'n_sigeff') %>%
    arrange(tax_ID) %>%
    dplyr::mutate(pct_sigeff = n_sigeff/total_sigeff*100) %>% 
    ungroup()

taxID$maj_eff_taxa <- maj_effect_taxa$maj_eff_taxa[match(taxID$tax_ID,maj_effect_taxa$tax_ID)]

maj_effect2_taxa$maj_eff_taxa <- NA
maj.table.taxa <- as.data.frame(cbind(maj_effect_taxa$tax_ID, maj_effect_taxa$maj_eff_taxa))


maj.table.taxa<-maj.table.taxa[!duplicated(maj.table.taxa),]


maj_effect2_taxa$maj_eff_taxa <- maj.table.taxa$V2[match(maj_effect2_taxa$tax_ID,maj.table.taxa$V1)]

# Deal with ties

for (i in 1:nrow(maj_effect2_taxa)){
  
    x <- maj_effect2_taxa[which(maj_effect2_taxa$tax_ID == maj_effect2_taxa$tax_ID[i]), 5]
    ifelse(var(x) == 0, maj_effect2_taxa$maj_eff_taxa[i] <- 'Mixed', maj_effect2_taxa$maj_eff_taxa[i] <- maj_effect2_taxa$maj_eff_taxa[i])
  }

write.csv(maj_effect2_taxa, paste0(tab.dir, 'maj_effect_taxa.csv'))

maj_effect3 <- cbind(maj_effect2_taxa$tax_ID,maj_effect2_taxa$maj_eff_taxa)
maj_effect3 <- as.data.frame(maj_effect3)
maj_effect3 <- maj_effect3[!duplicated(maj_effect3),]

taxID$maj_eff_taxa <- maj_effect3$V2[match(taxID$tax_ID, maj_effect3$V1)]



```

# 7. Export table

The table to be exported here will be used in another script for synthesis, data summaries and figures.

```{r}
# save as csv
  write.csv(s23, paste0(dat.dir,'s23.csv'), row.names = FALSE)
  write.csv(taxID, paste0(dat.dir,'tax_eff.csv'), row.names = FALSE)

```

