---
title: 'MCBD: Survey 2 and 3 Merge for Metacoupled Effects on Biodiversity'
<<<<<<< HEAD
author: "Veronica F. Frans, CSIS Lab, Michigan State University"
date: "May 30, 2020 (Updated: September 4, 2020)"
=======
author: "Ciara Hovis & Veronica F. Frans, CSIS Lab, Michigan State University"
date: "May 30, 2020 (Updated: September 16, 2020)"
>>>>>>> 816b281376cfaedda9499d772ff39ab6853d6784
output: 
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Methods summary

Synthesis of survey 2 and 3 results for metacoupling/biodiversity systematic review. It consists of error checks, response summaries, and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.2; R Core Team 2020) and its packages.

Load libraries, directories, and custom functions from source file.

```{r}
# Source file
  source('Reference.R')
```

Data is stored here:

```{r, echo=FALSE}
# Data directory
  dat.dir
```

Final tables are stored here:

```{r, echo=FALSE}
# Final tables
  tab.dir
```

Final figures are stored here:

```{r, echo=FALSE}
# Final figures
  fig.dir
```

For **this run** of the script, tables for manual checks will be stored in the following folder:

```{r, echo=FALSE}
tab.check.dir
```

# 3. Load data

THE SURVEY 2 NEEDS TO BE UPDATED --- CURRENTLY USING VERSION FROM 7/7

```{r}
# load previous workspace (if needed)
  #load("synthesisResults.RData")

# surveys
  survey2 <- read.csv(paste0(dat.dir,'survey2_cleaned_20200707.csv'))
  survey3 <- read.csv(paste0(dat.dir,'survey3_cleaned.csv'))
```

# 4. Data formatting

## 4.1 Merge tables

Merge tables. The expected length of this merge should be the same as survey 3, with fields from survey 2 repeated across entries for each paper id. 

```{r}
# left join survey 2 to survey 3
  s23 <- left_join(survey3,survey2,by=c("paper_id","coder_id"))
```

Show column names

```{r}
# get col names
  colnames(s23)
```

Drop columns. Includes s3 notes now.

```{r}
unwanted <- c(# survey 3 fields
              'timestamp.x','taxa.x',
              # survey 2 fields
              'coder_id','entry','final_decision','X',
              'taxa.y', 'timestamp.y', 'year_pub', 'author',
              'taxa_list', 'num_time_pd', 'year_start',
              'year_end','temp_res','temp_res_unk',
              'b4_dur_after','comments','further_discuss'
              )

s23$taxa <- s23$taxa.x
s23$sig_effect <- '' #adding column now because there are errors below

s23 <- s23 %>%
        select(-one_of(unwanted))
```

## 4.2 Quick cleanup of levels

Next, show levels of couplings

```{r}
levels(as.factor(s23$tele_cat))
```

**IMPORTANT STEP HERE:** 

Duplicate rows with multiple flow types. This means that effects and other results will be *duplicated* as well!!!!!!!!!!!!!!!!!!!!!!!!! 

The reason for doing this is so that we can attribute biodiversity impacts to the specific flows that may have been studied together, and whose individual impacts cannot be decoupled.

```{r}
# set as character
  s23$tele_cat <- as.character(s23$tele_cat)

# show original length of rows
  print(paste('Original number of rows:',nrow(s23)))

# split multiple flows listed in a row into other new rows
  s23 <- separate_rows(s23, tele_cat, sep=";", convert = TRUE)
  s23$tele_cat <- as.factor(s23$tele_cat)
  
# show new length of rows
  print(paste('Number of rows after separating multiple flows per paper:',nrow(s23)))

# show levels
  summary(s23$tele_cat)
```

Some have NA's. Let's see which ones they are.

```{r}
s23[is.na(s23$tele_cat),]
```

These items above are the **common survey** responses from Survey 2. This **needs to be addressed by the Survey 2 sub-team.**

# 6. Classify Impact and Significance Category

To simplify our results, we opted classify impacts into 4 categories:  Positive, Negative, Comp. Change, No relation or unclear.

## 6.1 Investigate Significance Not Evaluated

No action taken yet, need to discuss with group

```{r}
# Check how many entries were "not evaluated" n=259
table(s23$significant)

# subset and drop last row (all NAs)
not.eval <- s23[s23$significant == "Not evaluated",]
not.eval <- not.eval[-nrow(not.eval),]
  
# How many paper IDs? n=57
length(unique(not.eval$paper_id))
unique(not.eval$paper_id)

# Look at impacts and metric type
table(not.eval$biodiv_cat_1sp)
table(not.eval$biodiv_cat_multsp)
table(not.eval$biodiv_cat_habitat)
table(not.eval$effect)

```


## 6.2  Classification Code

```{r}

  for(i in 1:nrow(s23)) {
  
    # positive impact AND True/NotEval Sig == POSITIVE
    if(s23$effect[i] == 'Positive (beneficial)' &&
       (s23$significant[i] == 'TRUE' || s23$significant[i] == 'Not evaluated') )
    {
    s23$sig_effect[i] = 'Positive';
    }

    # negative impact AND True/NotEval Sig == NEGATIVE
    else if(s23$effect[i] == 'Negative (detrimental)' &&
       (s23$significant[i] == 'TRUE' || s23$significant[i] == 'Not evaluated') )
    {
    s23$sig_effect[i] = 'Negative';
    }

    # changed impact AND True/NotEval Sig == CHANGED
    else if(s23$effect[i] == 'Changed (e.g. species composition)' &&
    (s23$significant[i] == 'TRUE' || s23$significant[i] == 'Not evaluated') )
    {
    s23$sig_effect[i] = 'Changed';
    }

    else
    {
    s23$sig_effect[i] = 'No relation or unclear';
    }

  }

# Check if loop worked

check_sig_effect <- as.data.frame(cbind(s23$effect, s23$significant, s23$sig_effect))

# Look at distribution

table(s23$sig_effect)

```


# 7. Export table

The table to be exported here will be used in another script for synthesis, data summaries and figures.

```{r}
# save as csv
  write.csv(s23, paste0(dat.dir,'s23.csv'), row.names = FALSE)
```

