---
title: "Results_Survey2_cleanup"
author: "Yingjie Li"
date: "6/4/2020"
output:
  html_document:
    keep_tex: yes
    toc: yes
    toc_depth: 4
    toc_float: true
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE, cache.comments = FALSE,
                      warning = FALSE, message = FALSE, results='hold')
```

# 1. Methods summary

Synthesis of survey 3 results for metacoupling/biodiversity systematic review. It consists of error checks, response summaries, and visualizations of the accepted papers.

# 2. R Setup

The script presented here was done using R (version 4.0.2; R Core Team 2020) and its packages.

Load libraries, directories, and custom functions from source file.

```{r}
# Source file
  source('./scripts/Reference.R')
```

Data is stored here:

```{r, echo=FALSE}
# Data directory
  dat.dir
```

Final tables are stored here:

```{r, echo=FALSE}
# Final tables
  tab.dir
```

Final figures are stored here:

```{r, echo=FALSE}
# Final figures
  fig.dir
```

For **this run** of the script, tables for manual checks will be stored in the following folder:

```{r, echo=FALSE}
tab.check.dir
```



# 3. Load data

```{r}
csv     <- paste0(dat.dir, 'survey_cleanup/survey2_for_cleanup.csv');csv  ### all coded data, except the 5 common papers
csv.com <- paste0(dat.dir, 'common_papers/survey2_5_common_paper_selection_090120.csv');csv.com ### the 5 common papers

s2_sur <- read.csv(csv,     stringsAsFactors = F) # %>% select(-X)
s2_com <- read.csv(csv.com, stringsAsFactors = F) 
names(s2_sur)
names(s2_com)

### check col names in two df
names(s2_com) %in% names(s2_sur)
tt <- names(s2_sur) %in% names(s2_com); tt
!tt
names(s2_sur)[!tt] ## get the col names not included in the common paper data

### add those cols that were missing
s2_com_update <- s2_com %>%
  mutate(
    timestamp = 'common paper',
    coder_id = 'common paper',
    num_countries = 'common paper',
    scale_entire = 'common paper', 
    num_time_pd = 'common paper', 
    year_start = 'common paper',  
    year_end = 'common paper', 
    temp_res = 'common paper',
    temp_res_unk= 'common paper', 
    b4_dur_after= 'common paper', 
    peri_tele_flows= 'common paper',
    peri_tele_sep= 'common paper', 
    peri_tele_sep_unk= 'common paper', 
    scale_biodiv= 'common paper', 
    list_biodiv_metrics= 'common paper', 
    further_discuss= 'common paper',
  )
  # select(-c(num_countries))
### reorder the col by names
s2_com_update2 <- s2_com_update[, names(s2_sur)]

### row bind two data
survey2_cleanup <- rbind(s2_sur, s2_com_update2)
```


# 4. Data cleanup

## 4.2 Survey 2

### 4.2.1 Pre-Cleaning
  
```{r}
### Columns kept for analysis
names(survey2_cleanup)
# cols_remove <- c("timestamp", "coder_id", "author")
df0 <- survey2_cleanup %>%
  # dplyr::select(-cols_remove) %>%
  dplyr::mutate(
    taxa = gsub(',', ';', taxa_list),
    list_countries   = gsub('India\\;\\;', 'India\\;', list_countries),
    list_countries   = gsub(',', ';', list_countries),
    biodiv_countries = gsub(',', ';', biodiv_countries),
    biodiv_countries = trimws(biodiv_countries),
    )


### unify the answers
df1 <- df0 %>%  dplyr::mutate(
  data_type_biodiv=gsub('biological\\;', "Biological field observations;",
                        data_type_biodiv),
  data_type_biodiv=gsub('\\;rs', "\\;Remote sensing",
                        data_type_biodiv),
  data_type_biodiv=gsub('\\;aggregate', "\\;Aggregate institutional data",
                        data_type_biodiv),
  data_type_biodiv=gsub(';', ',', data_type_biodiv),
  data_type_biodiv=ifelse(data_type_biodiv=="biological", 
                          "Biological field observations",
                          data_type_biodiv))



dm_ls <- c('Field observations', 
           'Social science field surveys',
           'Remote sensing',
           'Aggregate institutional data'
           )


df2 <- df1 %>% dplyr::mutate(
  data_type_meta=gsub('biological', 'Field observations', data_type_meta),
  data_type_meta=gsub('Social science field surveys', 
                      'social', data_type_meta),
  data_type_meta=gsub('\\;aggregate', 
                      '\\;Aggregate institutional data',  data_type_meta),
  data_type_meta=gsub('social', 
                      'Social science field surveys', data_type_meta),
  data_type_meta=gsub(';', ',', data_type_meta),
  data_type_meta= trimws(data_type_meta),
  data_type_meta = ifelse(data_type_meta%in%dm_ls, data_type_meta, 'Other'),
  
  data_source_biodiv=gsub(';', ',', data_source_biodiv),
  data_source_meta  =gsub(';', ',', data_source_meta),
  
  taxa = gsub('Plants\\/trees\\/shrubs', 'Plants', taxa),
  taxa = gsub('Not specified|\\/global study', '', taxa),
  taxa = trimws(taxa), ## Remove leading and/or trailing whitespace
  taxa = ifelse(taxa == '', "Other", taxa),
  taxa = ifelse(paper_id == 292, "Fish", taxa),
  
  )

### an easy-to-use name for the following analysis
df   <- df2

### a copy for updating the df, will be the final result dataframe
df99 <- df
```


### 4.2.2 Deep-clean
```{r for test use, eval=FALSE, include=FALSE}
############ test code ############################
# # col_name <- 'list_continents'
# dt <- conti2
# 
# dw1 <- dt %>%
#   spread(key = 'key', value = 3) %>%
#   dplyr::mutate(na_col = NA) 
# ## as an assistant col, as some data only have one col
# 
# dw1[is.na(dw1)] <- ""  ## NA as ''
# dw2 <- matrix(apply(dw1[,2:ncol(dw1)],1,paste,collapse=";"),ncol=1) %>%
#   as.data.frame() %>%
#   dplyr::mutate(V2 = gsub('\\;\\;', '', V1),
#                 V2 = sub('\\;$', '', V2))
# 
# df99 <- dw2 %>%
#   dplyr::select(2) %>%
#   rename(c('V2' = col_name)) %>%
#   cbind(., dw1) %>%
#   dplyr::select(1:2) %>%
#   right_join(., df[, !names(df) %in% col_name],
#              by = 'paper_id') ## remove the old, and join
```


```{r function}
func_update_col <- function(dt, col_name){
  ### 1st, long table to wide one
  dw1 <- dt %>%
    spread(key = 'key', value = 3)  %>% ## the 3rd column 
    dplyr::mutate(na_col = NA)          ## as an assistant col, as some data only have one col
  
  dw1[is.na(dw1)] <- ""                 ## NA as ''
  dw2 <- matrix(apply(dw1[,2:ncol(dw1)],1,paste,collapse=";"),ncol=1) %>% 
    as.data.frame() %>%
    dplyr::mutate(V2 = gsub('\\;\\;', '', V1),
                  V2 = sub('\\;$', '', V2))
  ### to update the df
  df99 <- dw2 %>% 
    dplyr::select(2) %>%
    rename(c('V2' = col_name)) %>%
    cbind(., dw1) %>%
    dplyr::select(1:2) %>%
    right_join(., df99[, !names(df99) %in% col_name], 
               by = 'paper_id') ## remove the old, and join
  return(df99)
  
}
  

# df99 <- func_update_col(dt = taxa2, col_name = 'taxa')  
```

#### - taxa
```{r}
### taxa ---------------------------------------------------------------------
unique(df$taxa_list)
unique(df$taxa)

taxa0 <- df %>% select(paper_id, taxa)
taxa1 <- data.frame(taxa0, do.call(rbind, str_split(taxa0$taxa,';'))) 


ls.taxa <- c(
  "Amphibians", "Birds", "Fish", 
  "Invertebrates", "Mammals", 
  "Other", 
  "Plants", "Reptiles"     
)


taxa2 <- taxa1 %>%
  gather(key = 'key', value = taxa, 3:ncol(.)) %>%
  dplyr::mutate(
  #   taxa = gsub('Plants\\/trees\\/shrubs', 'Plants', taxa),
  #   taxa = gsub('Not specified|\\/global study', '', taxa),
    taxa = trimws(taxa), ## Remove leading and/or trailing whitespace
    taxa = ifelse(taxa%in%ls.taxa, taxa, 'Other'),
  #   taxa = ifelse(taxa == '', "Other", taxa)
  ) %>%
  distinct(paper_id, taxa, .keep_all = T)

sort(unique(taxa2$taxa))

## taxa percentage = taxa studies/total number of the papers
n_paper <- length(unique(df$paper_id)); n_paper
taxa2 %>%
  group_by(taxa) %>%
  tally() %>%
  mutate(pct = n/n_paper * 100) %>%
  arrange(pct)
```


#### - continents
```{r}
a <- 'North America \\(includes Hawaii \\& all countries above Panama Canal\\)'
b <- 'Oceania \\(Australia\\, New Zealand\\, Fiji\\, etc\\)'

conti0 <- df %>% select(paper_id, list_continents) %>%
  dplyr::mutate(
    list_continents = gsub(a, 'North America', list_continents),
    list_continents = gsub(b, 'Oceania', list_continents)
  )
unique(conti0$list_continents)
unique(conti0$list_continents)

conti1 <- data.frame(conti0, do.call(rbind, str_split(conti0$list_continents,','))) 

conti2 <- conti1 %>%
  gather(key = 'key', value = list_continents, 3:ncol(.)) %>%
  dplyr::mutate(
    list_continents = trimws(list_continents) ## Remove leading and/or trailing whitespace
    ) %>%
  distinct(paper_id, list_continents, .keep_all = T)

conti2 %>%
  group_by(list_continents) %>%
  tally() %>%
  mutate(pct = n/n_paper * 100) %>%
  arrange(pct) #%>%
  # ggplot()+
  # geom_col(aes(x=list_continents, y=pct))


df99 <- func_update_col(dt = conti2, col_name = 'list_continents')

```



#### - habitat
```{r}
h0 <- df %>% select(paper_id, habitat) 

unique(h0$habitat)

h1 <- data.frame(h0, do.call(rbind, str_split(h0$habitat,','))) 

h2 <- h1 %>%
  gather(key = 'key', value = habitat, 3:ncol(.)) %>%
  dplyr::mutate(
    habitat = trimws(habitat) ## Remove leading and/or trailing whitespace
    ) %>%
  distinct(paper_id, habitat, .keep_all = T)

h2 %>%
  group_by(habitat) %>%
  tally() %>%
  mutate(pct = n/n_paper * 100) %>%
  arrange(pct) #%>%


df99 <- func_update_col(dt = h2, col_name = 'habitat')
```



####    - data type
#####   -- data_type_biodiv
```{r}
### data_type_biodiv --------------------------------------------------------
unique(df2$data_type_biodiv)
unique(df2$data_type_meta)

db_ls <- c('Biological field observations', 
           'Social science field observations',
           'Remote sensing',
           'Aggregate institutional data'
           )

db0 <- df2 %>% select(paper_id, data_type_biodiv) 
db1 <- data.frame(db0, do.call(rbind, str_split(db0$data_type_biodiv,','))) 
db2 <- db1 %>%
  gather(key = 'key', value = data_type_biodiv, 3:ncol(.)) %>%
  dplyr::mutate(
    data_type_biodiv = trimws(data_type_biodiv),
    data_type_biodiv = ifelse(data_type_biodiv %in% db_ls, 
                              data_type_biodiv, 'Other')
    ) %>%
  distinct(paper_id, data_type_biodiv, .keep_all = T)

db2 %>%
  group_by(data_type_biodiv) %>%
  tally() %>%
  mutate(pct = n/n_paper * 100) %>%
  arrange(pct) #%>%


df99 <- func_update_col(dt = db2, col_name = 'data_type_biodiv')
```

#####   -- data_type_meta
```{r}
### data_type_meta --------------------------------------------------------
dm0 <- df2 %>% select(paper_id, data_type_meta) 
# dm1 <- data.frame(dm0, do.call(rbind, str_split(dm0$data_type_meta,','))) 
dm1 <- dm0

dm_ls <- c('Field observations', 
           'Social science field surveys',
           'Remote sensing',
           'Aggregate institutional data'
           )
dm2 <- dm1 %>%
  # gather(key = 'key', value = data_type_meta, 3:ncol(.)) %>%
  dplyr::mutate(
    key = 'NA',
    data_type_meta = trimws(data_type_meta),
    data_type_meta = ifelse(data_type_meta%in%dm_ls, data_type_meta, 'Other'),
    
    ) %>%
  select(1,3,2) %>%
  distinct(paper_id, data_type_meta, .keep_all = T)

unique(dm2$data_type_meta)

dm2 %>%
  group_by(data_type_meta) %>%
  tally() %>%
  mutate(pct = n/n_paper * 100) %>%
  arrange(pct) #%>%
  

df99 <- func_update_col(dt = dm2, col_name = 'data_type_meta')

```


####    - tele_cat
```{r}

tc0 <- df %>% select(paper_id, tele_cat) %>%
  dplyr::mutate(
    tele_cat = ifelse(paper_id==1616, 'Knowledge Transfer,Investment',
                      tele_cat))

# Apply Animal migration tele_cat fix - CLH (9/23/2020)
tc0$tele_cat[tc0$paper_id == '4518'] <- 'Trade, Knowledge Transfer' # Remove 'Migration (non-human)'
tc0$tele_cat[tc0$paper_id == '2642'] <- 'Species Dispersal' 
tc0$tele_cat[tc0$paper_id == '3151'] <- 'Energy Transfer'
tc0$tele_cat[tc0$paper_id == '3511'] <- 'Species Dispersal' 
tc0$tele_cat[tc0$paper_id == '5804'] <- 'Species Dispersal'


# Fix lingering "other" categories (based on CLH recommendation - 9/23/2020)
tc0$tele_cat[tc0$paper_id == '44'] <- 'Knowledge Transfer, Investment' # conservation program/policy
tc0$tele_cat[tc0$paper_id == '1040'] <- 'Energy Transfer' # oil spil
tc0$tele_cat[tc0$paper_id == '5175'] <- 'Knowledge Transfer, Investment' # conservation program/policy


unique(df$tele_cat)
str(tc0)

tc1 <- data.frame(tc0, do.call(rbind, str_split(tc0$tele_cat,','))) %>%
  select(-tele_cat)

tc_ls <- c(
  'Trade',
  'Migration (human)',
  'Migration (non-human)',
  'Species Dispersal',
  'Tourism',
  'Knowledge Transfer',
  'Technology Transfer',
  'Investment',
  'Water Transfer',
  'Waste Transfer',
  'Energy Transfer'
)

tc2 <- tc1 %>%
  gather(key = 'key', value = tele_cat, 2:ncol(.)) %>%
  dplyr::mutate(
    ### based on Aurora's double-check
    tele_cat = ifelse(paper_id==227,  'Trade', tele_cat),
    tele_cat = ifelse(paper_id==92,  'Trade', tele_cat),
    tele_cat = ifelse(paper_id==3697,  'Trade', tele_cat),
    tele_cat = ifelse(paper_id==4832,  'Trade', tele_cat),
    tele_cat = ifelse(paper_id==396,  'Tourism', tele_cat),
    
    tele_cat = ifelse(paper_id==292,  'Species Dispersal', tele_cat),
    tele_cat = ifelse(paper_id==2050,  'Species Dispersal', tele_cat),
    
    tele_cat = ifelse(paper_id==6396,  'Waste Transfer', tele_cat),
    ) %>%
  
  dplyr::mutate(
    tele_cat = gsub('Migration nonhuman', 'Migration (non-human)', tele_cat),
    tele_cat = gsub('.*trade.*', 'Trade', tele_cat),
    tele_cat = gsub('.*Water.*', 'Water Transfer', tele_cat),
    tele_cat = gsub('.*introduction.*|.*nvasive.*', 'Migration (non-human)', tele_cat),
    
    
    tele_cat = trimws(tele_cat) ## Remove leading and/or trailing whitespace
    ) %>%
  distinct(paper_id, tele_cat, .keep_all = T) %>%
  mutate(
    tele_cat_ori = tele_cat,
    tele_cat     = ifelse(tele_cat%in%tc_ls, tele_cat, 'Other')) %>%
  ### based on Aurora's double-check
  mutate(tele_cat = ifelse(paper_id %in% c(3335, 109, 1752, 2704, 6493, 4207), 
                            'remove', tele_cat)) %>%
  dplyr::filter(tele_cat != 'remove')

### check "Other" in tc_cat
tc2_check <- tc2 %>%
  dplyr::filter(tele_cat     == 'Other', 
                tele_cat_ori != 'Other')
fname <- paste0(dat.dir, '/survey2_tc_cat_check.csv'); fname
# write.csv(x = tc2_check, file = fname, row.names = F)


### summarize results and update this survey response
tc2 <- tc2 %>% dplyr::select(-tele_cat_ori)
sort(unique(tc2$tele_cat))

tc2 %>%
  group_by(tele_cat) %>%
  tally() %>%
  mutate(pct = n/n_paper * 100) %>%
  arrange(desc(pct)) #%>%

df99 <- func_update_col(dt = tc2, col_name = 'tele_cat')
```


####    - data source
#####   -- data_source_biodiv

```{r}

dsb0 <- df %>% select(paper_id, data_source_biodiv) 

unique(df$data_source_biodiv)

dsb1 <- data.frame(
  dsb0, do.call(rbind, str_split(dsb0$data_source_biodiv,','))) %>%
  select(-data_source_biodiv)

dsb2 <- dsb1 %>%
  gather(key = 'key', value = data_source_biodiv, 2:ncol(.)) %>%
  dplyr::mutate(
    data_source_biodiv = trimws(data_source_biodiv) 
    ) %>%
  distinct(paper_id, data_source_biodiv, .keep_all = T)

dsb2 %>%
  group_by(data_source_biodiv) %>%
  tally() %>%
  mutate(pct = n/n_paper * 100) %>%
  arrange(pct) #%>%

df99 <- func_update_col(dt = dsb2, col_name = 'data_source_biodiv')
```




#####    -- data_source_meta
```{r}
dsm0 <- df %>% select(paper_id, data_source_meta) 

unique(df$data_source_meta)

dsm1 <- data.frame(
  dsm0, do.call(rbind, str_split(dsm0$data_source_meta,','))) %>%
  select(-data_source_meta)

dsm2 <- dsm1 %>%
  gather(key = 'key', value = data_source_meta, 2:ncol(.)) %>%
  dplyr::mutate(
    data_source_meta = trimws(data_source_meta) 
    ) %>%
  distinct(paper_id, data_source_meta, .keep_all = T)

dsm2 %>%
  group_by(data_source_meta) %>%
  tally() %>%
  mutate(pct = n/n_paper * 100) %>%
  arrange(pct) #%>%
df99 <- func_update_col(dt = dsm2, col_name = 'data_source_meta')

```





####    - list_countries

```{r EU}
eu <- c(
  'AUT',	'BEL',	'BGR',	'HRV',	'CYP',	'CZE',	'DNK',	'EST',	'FIN',	'FRA',	'DEU',
  'GRC',	'HUN',	'IRL',	'ITA',	'LVA',	'LTU',	'LUX',	'MLT',	'NLD',	'POL',	'PRT',
  'ROU',	'SVK',	'SVN',	'ESP',	'SWE',	'GBR')

length(eu)

eue <- "'AUT';	'BEL';	'BGR';	'HRV';	'CYP';	'CZE';	'DNK';	'EST';	'FIN';	'FRA';	'DEU';	'GRC';	'HUN';	'IRL';	'ITA';	'LVA';	'LTU';	'LUX';	'MLT';	'NLD';	'POL';	'PRT';	'ROU';	'SVK';	'SVN';	'ESP';	'SWE';	'GBR'"

eue <- gsub("\t|\\'", '', eue); eue
```



```{r}
c0 <- df %>% select(paper_id, coder_id, list_countries) %>% 
  ### contact coder and update 
  dplyr::mutate(
    list_countries = ifelse(paper_id==109,  'Costa Rica', list_countries),
    list_countries = ifelse(paper_id==566,  'Nepal', list_countries),
    list_countries = ifelse(paper_id==1893, 'China', list_countries),
    list_countries = ifelse(paper_id==2036, 'Indonesia', list_countries),
    list_countries = ifelse(paper_id==3081, 'Romanaia', list_countries),
    list_countries = ifelse(paper_id==4136, 'China', list_countries),
    list_countries = ifelse(paper_id==4427, 'Canada', list_countries),
    list_countries = ifelse(paper_id==4772, 'Nepal', list_countries),
    ## Anna
    list_countries = ifelse(paper_id==5477, 'Indonesia', list_countries),
    list_countries = ifelse(paper_id==5875, 'Brazil', list_countries),
    ## Ciara, Emily
    list_countries = ifelse(paper_id==6511, 'Unclear', list_countries),
    list_countries = ifelse(paper_id==5844, 'Solomon Islands', list_countries),
    ## Ming Lei
    list_countries = ifelse(paper_id==713, 'Many', list_countries),
    list_countries = ifelse(paper_id==1681, 'Bulgaria', list_countries),
    list_countries = ifelse(paper_id==396, 'Australia', list_countries),
    list_countries = ifelse(paper_id==2284, 'Botswana; South Africa; Zimbabwe', list_countries),
    list_countries = ifelse(paper_id==4574, 'Mongolia; India; China', list_countries),
    
    list_countries = ifelse(paper_id==6948, 'Brazil', list_countries),
    list_countries = ifelse(paper_id==6502, 'Canada; USA', list_countries),
    list_countries = gsub(' and ', ';', list_countries),
    # list_countries = ifelse(paper_id==4772, 'Nepal', list_countries),
 
  ) #%>%
  # dplyr::filter(paper_id != 109)

unique(df$list_countries)

### split the country names to multiple columns 
c1 <- data.frame(
  c0, do.call(rbind, str_split(c0$list_countries,';'))) #%>%
  # select(-list_countries)

c2 <- c1 %>%
  gather(key = 'key', value = list_countries, 4:ncol(.)) %>%
  dplyr::mutate(
    list_countries = trimws(list_countries),
    list_countries = str_to_title(list_countries)
    
    ) %>%
  dplyr::distinct(paper_id, list_countries, .keep_all = T) %>% 
  as.data.frame() %>%
  # dplyr::mutate(id = paste0(paper_id, substr(list_countries, 1,3))) %>%
  dplyr::mutate(
    list_countries=gsub('Usa|United States', 'United States of America', list_countries),
    list_countries=gsub('Russia', 'Russian Federation', list_countries),
    list_countries=gsub('Romanaia', 'Romania', list_countries),
    list_countries=gsub('Tanzania', 'United Republic of Tanzania', list_countries),
    list_countries=gsub('Ethopia', 'Ethiopia', list_countries),
    list_countries=gsub('St Lucia', 'Bolivia (Plurinational State of)', list_countries),
    list_countries=gsub('Republic Of Maldives', 'Maldives', list_countries),
    list_countries=gsub('.*Rest Of The World.*', 'Rest Of The World', list_countries),
    list_countries=gsub('.*Bolivia.*', 
                        'Bolivia (Plurinational State of)', list_countries),
    list_countries=gsub('.*Brazil.*', 'Brazil', list_countries),
    list_countries=gsub('.*Eu.*', 'EUE', list_countries),
    list_countries=gsub('.*Antarctic.*', 'Antarctica', list_countries),
    list_countries=gsub('.*Many.*', 'Many', list_countries),
  )

c2_unique <- c2 %>%
  distinct(list_countries, .keep_all = T) %>%
  arrange(list_countries)
getwd()
fname <- paste0(dat.dir); fname
# write_xlsx(c2_unique, "_list_countries_4Coding.xlsx")

### read in coded country names
ctr <- readxl::read_excel(paste0(dat.dir, '_Country codes_names.xlsx'), 1, "A1:B283") 

### join the two data
c3 <- merge(c2, ctr, by.x='list_countries', by.y='ctr_fao', all.x=T) %>%
  dplyr::mutate(
    iso_fao = ifelse(list_countries == 'Rest Of The World', 'ROW', iso_fao),
    iso_fao = ifelse(list_countries == 'Antarctica', 'ATA', iso_fao),
    iso_fao = ifelse(list_countries == 'EUE', 'EUE', iso_fao),
    iso_fao = ifelse(list_countries == '2', 'Many', iso_fao),
    iso_fao = ifelse(list_countries == '35', 'Many', iso_fao),
    # iso_fao = ifelse(is.na(iso_fao), 'Unclear', iso_fao),
  ) %>%
  arrange(!is.na(iso_fao), iso_fao, list_countries) 

### check data with coder
c3_check <- c3 %>%
  dplyr::select(-coder_id) %>%
  filter(is.na(iso_fao)) %>%
  filter(list_countries != 'Many') %>%
  left_join(x = ., y= df99[, c('coder_id', 'paper_id')], by = "paper_id") %>%
  arrange(coder_id, paper_id)
c3_check$list_countries
fname <- paste0(dat.dir, 'CHECK_THIS_MANUALLY--survey2_list_countries_check.csv'); fname
write.csv(x = c3_check, file = fname, row.names = F)

c4 <- c3 %>%
  dplyr::mutate(list_countries = iso_fao,
                # key = iso_fao,
                ) %>% 
  dplyr::select(-iso_fao) %>%
  dplyr::select(paper_id, key, list_countries) %>%
  dplyr::mutate(list_countries = ifelse(
    list_countries=='EUE', eue, list_countries))
### 
df99 <- func_update_col(dt = c4, col_name = 'list_countries')

```




####    - biodiv_countries
```{r}
bc0 <- df %>% select(paper_id, biodiv_countries) %>%
  dplyr::mutate(
    
    # ## Ruishan
    # biodiv_countries = ifelse(paper_id==109,  'Costa Rica', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==566,  'Nepal', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==854,  'USA', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==1893,  'China', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==2036,  'Indonesia', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==2214,  'Chile', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==2402,  'Indonesia', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==2504,  'China', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==3081,  'Romanaia', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==4136,  'China', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==4207,  'India', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==4427,  'Canada', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==4772,  'Nepal', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==6348,  'Germany', biodiv_countries),
    # biodiv_countries = ifelse(paper_id==3790002,  'China', biodiv_countries),
    
    ## anna
    biodiv_countries = ifelse(paper_id==5477,  'Indonesia', biodiv_countries),
    biodiv_countries = ifelse(paper_id==5875,  'Brazil', biodiv_countries),
    
    ## yuqian
    biodiv_countries = ifelse(paper_id==4209,  'many', biodiv_countries),
    
    ## yingjie
    biodiv_countries = ifelse(paper_id==2222,  'many', biodiv_countries),
    
    ##
    biodiv_countries = ifelse(paper_id==45,  'Brazil', biodiv_countries),
    biodiv_countries = ifelse(paper_id==92,  'remove', biodiv_countries),
    biodiv_countries = ifelse(paper_id==332,  'Ethiopia', biodiv_countries),
    biodiv_countries = ifelse(paper_id==357,  'Canada', biodiv_countries),
    biodiv_countries = ifelse(paper_id==523,  'Many', biodiv_countries),
    
    biodiv_countries = ifelse(paper_id==654,  'Spain', biodiv_countries),
    biodiv_countries = ifelse(paper_id==897,  'Slovakia; Poland', biodiv_countries),
    biodiv_countries = ifelse(paper_id==2546,  'EU', biodiv_countries),
    biodiv_countries = ifelse(paper_id==2606,  'Germany', biodiv_countries),
    biodiv_countries = ifelse(paper_id==2704,  'Cyprus', biodiv_countries),
    biodiv_countries = ifelse(paper_id==3151,  'France', biodiv_countries),
    biodiv_countries = ifelse(paper_id==3165,  'Italy', biodiv_countries),
    biodiv_countries = ifelse(paper_id==4087,  'USA', biodiv_countries),
    
    biodiv_countries = ifelse(paper_id==4132,  'Norway', biodiv_countries),
    biodiv_countries = ifelse(paper_id==4155,  'USA', biodiv_countries),
    biodiv_countries = ifelse(paper_id==4841,  'remove', biodiv_countries),
    biodiv_countries = ifelse(paper_id==5486,  'Spain', biodiv_countries),
    biodiv_countries = ifelse(paper_id==5905,  'Brazil', biodiv_countries),
    
    biodiv_countries = ifelse(paper_id==5966,'Brazil;Paraguay;Argentina;Bolivia;Uruguay',
                              biodiv_countries),
    biodiv_countries = ifelse(paper_id==6396,  'Belarus; Ukraine', biodiv_countries),
    biodiv_countries = ifelse(paper_id==6493,  'USA', biodiv_countries),
    biodiv_countries = ifelse(paper_id==6502,  'USA; Canada', biodiv_countries),
    biodiv_countries = ifelse(paper_id==6845,  'French Polynesia', biodiv_countries),

  )



### xing ying
xy     <- 'amendments and supplements from Emily Xing_v4.xlsx'
xy.xls <- paste0(dat.dir, xy); xy.xls
xy <- readxl::read_excel(xy.xls) %>%
  dplyr::select(c(1, countries_bio)) %>%
  dplyr::filter(!is.na(countries_bio))
names(xy) <- c('paper_id', 'biodiv_countries')


### filter out xing ying's data
bc01 <- bc0 %>% 
  dplyr::filter(biodiv_countries !='no such data in Chinese survey')
bc02 <- bc0 %>% 
  dplyr::filter(biodiv_countries =='no such data in Chinese survey') %>%
  dplyr::select(-biodiv_countries) %>%
  left_join(., xy, by='paper_id')
bc0 <- rbind(bc01, bc02) %>%
  dplyr::mutate(
    biodiv_countries = gsub(',', ';', biodiv_countries),
    biodiv_countries = gsub(' and ', ';', biodiv_countries),
    biodiv_countries = gsub('3\\; ', '', biodiv_countries),
    biodiv_countries = gsub('25 EU countries', 'EUE', biodiv_countries)
  )


###
unique(bc0$biodiv_countries)

bc1 <- data.frame(
  bc0, do.call(rbind, str_split(bc0$biodiv_countries,';'))) #%>%
  # dplyr::select(-biodiv_countries)

bc2 <- bc1 %>%
  gather(key = 'key', value = biodiv_countries, 3:ncol(.)) %>%
  dplyr::mutate(
    biodiv_countries = trimws(biodiv_countries),
    biodiv_countries = str_to_title(biodiv_countries),
    ) %>%
  dplyr::distinct(paper_id, biodiv_countries, .keep_all = T) %>% 
  as.data.frame() %>%
  # dplyr::mutate(id = row_number())
  dplyr::mutate(
    biodiv_countries=gsub('Usa|United States', 'United States of America',
                          biodiv_countries),
    biodiv_countries=gsub('Russia', 'Russian Federation', biodiv_countries),
    biodiv_countries=gsub('Romanaia', 'Romania', biodiv_countries),
    biodiv_countries=gsub('Tanzania', 'United Republic of Tanzania', biodiv_countries),
    biodiv_countries=gsub('Ethopia', 'Ethiopia', biodiv_countries),
    biodiv_countries=gsub('Zimbabw', 'Zimbabwe', biodiv_countries),
    biodiv_countries=gsub('St Lucia', 'Bolivia (Plurinational State of)',
                          biodiv_countries),
    biodiv_countries=gsub('Republic Of Maldives', 'Maldives', biodiv_countries),
    biodiv_countries=gsub('.*Rest Of The World.*', 
                          'Rest Of The World', biodiv_countries),
    biodiv_countries=gsub('.*Bolivia.*', 
                        'Bolivia (Plurinational State of)', biodiv_countries),
    biodiv_countries=gsub('.*Brazil.*', 'Brazil', biodiv_countries),
    biodiv_countries=gsub('.*Eu.*', 'EUE', biodiv_countries),
    biodiv_countries=gsub('.*Antarctic.*', 'Antarctica', biodiv_countries),
    biodiv_countries=gsub('.*Many.*', 'Many', biodiv_countries),
  )

getwd()
fname <- paste0(dat.dir)
# write_xlsx(bc2, "_biodiv_countries_4Coding.xlsx")

bc3 <- merge(bc2, ctr, by.x='biodiv_countries', by.y='ctr_fao', all.x=T) %>%
  dplyr::mutate(
    iso_fao = ifelse(biodiv_countries == 'Rest Of The World', 'ROW', iso_fao),
    iso_fao = ifelse(biodiv_countries == 'Antarctica', 'ATA', iso_fao),
    iso_fao = ifelse(biodiv_countries == 'EUE', 'EUE', iso_fao),
    # iso_fao = ifelse(is.na(iso_fao), 'Unclear', iso_fao),
  ) %>%
  arrange(!is.na(iso_fao), iso_fao, biodiv_countries) 

### check data with coder
bc3_check <- bc3 %>%
  filter(is.na(iso_fao)) %>%
  filter(biodiv_countries != 'Many') %>%
  left_join(x = ., y= df99[, c('coder_id', 'paper_id')], by = "paper_id") %>%
  arrange(coder_id, paper_id)
fname <- paste0(dat.dir, 'CHECK_THIS_MANUALLY--survey2_biodiv_countries_check.csv'); fname
write.csv(x = bc3_check, file = fname, row.names = F)

bc4 <- bc3 %>%
  dplyr::mutate(bc3_check = iso_fao,
                # key = iso_fao,
                ) %>% 
  dplyr::select(-iso_fao) %>%
  dplyr::select(paper_id, key, bc3_check) %>% 
  dplyr::mutate(bc3_check = ifelse(
    bc3_check=='EUE', eue, bc3_check))
### 
df99 <- func_update_col(dt = bc4, col_name = 'biodiv_countries')
# df99 <- func_update_col(dt = dsm2, col_name = 'data_source_meta')

```



# 5. Save cleaned data to local
```{r}
today <- format(Sys.Date(), "%Y%m%d"); today
fname <- paste0(dat.dir, 'survey2_cleaned.csv'); fname; survey2_cleaned = fname
write.csv(x = df99, file = fname, row.names = F)
```


